### 2016-11-20 concept-slides.tex
wrote concept slides

\documentclass{beamer}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

\addtobeamertemplate{frametitle}{\let\insertframetitle\insertsubsectionhead}{}
\newcommand{\ft}{\frametitle{dummy}}

\begin{document}
\maketitle
\section{Introduction}
\begin{frame}
  \begin{itemize}
    \item Context
      \begin{itemize}
        \item What is modelled?
        \item How is it modelled?
      \end{itemize}
    \item Example
      \begin{itemize}
        \item Introducing an example which is used to illustrate different
          aspects throughout the presentation
        \item Interleaved graphs for two players, both want to acquire a
          spanning tree
      \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Game definition}
\begin{frame}
  \ft
  \begin{itemize}
    \item Formally define game
    \item Refer to the example
  \end{itemize}
\end{frame}
\subsection{Pure Nash equilibria}
\begin{frame}
  \ft
  \begin{itemize}
    \item Explain what PNEs are (maybe from previous presentations this
      knowledge can be assumed)
    \item Again the example can be used to illustrate what uniliteral change
      might imply
  \end{itemize}
\end{frame}
\subsection{Basic matroid theory}
\begin{frame}
  \ft
  \begin{itemize}
    \item Formally define matroids
    \item Explain the meaning of the definition by using the example
    \item Contraction and deletion (again with example)
    \item Define Matroid games (and mention that the example fits)
  \end{itemize}
\end{frame}

\section{Algorithm: PNE in Unweighted Matroid Games}
\subsection{Algorithm}
\begin{frame}
  \ft
  \begin{itemize}
    \item Present algorithm
    \item Execute one or two steps at example
  \end{itemize}
\end{frame}

\subsection{Correctness}
\begin{frame}
  \ft
  \begin{itemize}
    \item Intuitively present the ideas for the correctness
    \item (Formal proofs might take too long?)
  \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  \begin{itemize}
    \item Introduce socially optimal solution
    \item Show (or at least motivate) why this is a PNE
    \item Mention reduction to show that finding an optimal solution is NP-hard
  \end{itemize}
\end{frame}

\section{Non-Matroid Strategy Spaces}
\subsection{Lack of PNE}
\begin{frame}
  \ft
  \begin{itemize}
    \item Present that for Non-Matroid Games we can find strategy spaces
      which do not allow PNE
    \item Illustrate the construction by a picture
  \end{itemize}
\end{frame}

\subsection{Non-Decreasing Marginal Cost Functions \& Price of Anarchy}
\begin{frame}
  \ft
  \begin{itemize}
    \item Present that games with Non-Decreasing Marginal Cost Functions allow
      PNE (explain how the marginal cost pricing is obtained)
    \item Define Price of Anarchy
    \item Mention that non-increasing and non-decreasing games with weighted
      players is unbounded
  \end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}
  \begin{itemize}
    \item Sum up results
    \item Embed results into topic
  \end{itemize}
\end{frame}

\end{document}

### 2016-12-29 slides.tex
started on slides

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

\newcommand{\tupel}[1]{\left(#1\right)}
\newcommand{\set}[1]{\left{#1\right}}

\begin{document}
\maketitle
\section{Introduction}
\begin{frame}
  % \begin{itemize}
  %   \item Context (1 slide)
  %     \begin{itemize}
  %       \item What is modelled?
  %       \item How is it modelled?
  %     \end{itemize}
  %   \item Example (1 slide)
  %     \begin{itemize}
  %       \item Introducing an example which is used to illustrate different
  %         aspects throughout the presentation
  %       \item Interleaved graphs for two players, both want to acquire a
  %         spanning tree
  %     \end{itemize}
  % \end{itemize}
\end{frame}

\subsection{Game definition}
\begin{frame}
  \frametitle{Definition: congestion model}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item $N$: set of players
    \item $E$: set of resources
    \item $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
      set of desired resources $S_{i}\subseteq E$: set of configurations
    \item $d_{i}$: demand of player $i$ for her resource
      \begin{itemize}
        \item $d_{i} = 1$ for an unweighted game
        \item $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
          in configuration $S\in\mathcal{S}$
      \end{itemize}
    \item $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
      $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
      of $S$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Definition: weighted resource buying game}
  \begin{equation*}
    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
    \left(c_{e}\right)_{e\in E}}
  \end{equation*}
  \begin{equation*}
    \leadsto\mathcal{G} = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
  \end{equation*}
  \vspace{-1cm}
  \begin{itemize}
    \item $\mathcal{P}=\times_{i\in N} P_{i}$ with
      $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
    \item $e\in E$ is bought under $S\in \mathcal{S}$ if
      $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
    \item $\pi_{i}(S) =
      \begin{cases}
        \sum_{e\in E}p_{i}^{e} &\textit{if }S_{i}\textit{ is bought}\\
        \infty &\textit{otherwise}
      \end{cases}$: {private cost of player $i$}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{A few simplifications}
  \begin{itemize}
    \item \emph{unweighted} games
    \item marginally non-increasing cost-function $c_{e}$:
      \begin{equation*}
        c_{e}(x + \delta) - c_{e}(x) \geq c_{e}(y + \delta) - c_{e}(y)
        \;\;x\leq y, \delta \in \mathbb{N}
      \end{equation*}
      \begin{center}
        \begin{tikzpicture}
          \begin{axis}[
              xlabel=$x$,
              ylabel=$c_{e}(x)$,
              smooth,
              width=5cm,
              height=3cm,
              ticks=none,
              no markers
            ]
              \addplot{ln(x)};
          \end{axis}
        \end{tikzpicture}
      \end{center}
    \item restrict players demands to a specific mathematical structure:
      Matroids
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Definition: Matroid}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{equation*}
      M = (E, B)
    \end{equation*}
    \vspace{-0.8cm}
    \begin{itemize}
      \item $E$: ground-set
      \item $B$: set of bases
      \item \emph{basis exchange property}:
        \vspace{-1cm}
        \begin{center}
          \begin{align*}
            \forall &X, Y\in B:\\
            &\forall x\in (X\setminus Y)\\
            &\exists y\in (Y\setminus X):\\
            &\;(X\setminus \{x\})\cup\{y\}\in B
          \end{align*}
        \end{center}
    \end{itemize}
    \column{0.5\textwidth}
  \end{columns}
\end{frame}

\subsection{Pure Nash equilibria}
\begin{frame}
  % \begin{itemize}
  %   \item (1 slide)
  %   \item Explain what PNEs are (maybe from previous presentations this
  %     knowledge can be assumed)
  %   \item Again the example can be used to illustrate what uniliteral change
  %     might imply
  % \end{itemize}
% \end{frame}
% \subsection{Basic matroid theory}
% \begin{frame}
  % \begin{itemize}
  %   \item (2/3 slides)
  %   \item Formally define matroids
  %   \item Explain the meaning of the definition by using the example
  %   \item Contraction and deletion (again with example)
  %   \item Define Matroid games (and mention that the example fits)
  % \end{itemize}
\end{frame}

\section{Algorithm: PNE in Unweighted Matroid Games}
\subsection{Algorithm}
\begin{frame}
  % \begin{itemize}
  %   \item Present algorithm (2 slides)
  %   \item Execute one or two steps at example (only a slide but animation might
  %     take some time ca. 5 minutes)
  % \end{itemize}
\end{frame}

\subsection{Correctness}
\begin{frame}
  % \begin{itemize}
  %   \item Intuitively present the ideas for the correctness (1/2 slides)
  %   \item (Formal proofs might take too long?)
  % \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  % \begin{itemize}
  %   \item (2 slides)
  %   \item Introduce socially optimal solution
  %   \item Show (or at least motivate) why this is a PNE
  %   \item Mention reduction to show that finding an optimal solution is NP-hard
  % \end{itemize}
\end{frame}

\section{Non-Matroid Strategy Spaces}
\subsection{Lack of PNE}
\begin{frame}
  % \begin{itemize}
  %   \item (1 slide)
  %   \item Present that for Non-Matroid Games we can find strategy spaces
  %     which do not allow PNE
  %   \item Illustrate the construction by a picture
  % \end{itemize}
\end{frame}

\subsection{Non-Decreasing Marginal Cost Functions \& Price of Anarchy}
\begin{frame}
  % \begin{itemize}
  %   \item (3 slides)
  %   \item Present that games with Non-Decreasing Marginal Cost Functions allow
  %     PNE (explain how the marginal cost pricing is obtained)
  %   \item Define Price of Anarchy
  %   \item Mention that non-increasing and non-decreasing games with weighted
  %     players is unbounded
  % \end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}
  % \begin{itemize}
  %   \item (1 slide)
  %   \item Sum up results
  %   \item Embed results into topic
  % \end{itemize}
\end{frame}

\end{document}

### 2017-01-05 slides.tex
added slide on matroid operations
added cuts to matroids
added player 2 part of shared graph

@@
 \usepackage{tikz}
+\usepackage{csquotes}
 \usetheme{metropolis}
@@
 \newcommand{\tupel}[1]{\left(#1\right)}
-\newcommand{\set}[1]{\left{#1\right}}
+\newcommand{\set}[1]{\left\{#1\right\}}
 
 \begin{document}
+\input{tikz/settings}
 \maketitle
@@
             &\exists y\in (Y\setminus X):\\
-            &\;(X\setminus \{x\})\cup\{y\}\in B
+            &\;(X\setminus \set{x})\cup\{y\}\in B
           \end{align*}
@@
     \column{0.5\textwidth}
+    \uncover<2->{Spanning trees:}
+    \begin{center}
+      \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}\\[0.5cm]}
+      \uncover<3->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S1}}}
+      \uncover<4->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S2}}}
+      \uncover<5->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S3}}}
+    \end{center}
   \end{columns}
@@
 
-\subsection{Pure Nash equilibria}
 \begin{frame}
-  % \begin{itemize}
-  %   \item (1 slide)
-  %   \item Explain what PNEs are (maybe from previous presentations this
-  %     knowledge can be assumed)
-  %   \item Again the example can be used to illustrate what uniliteral change
-  %     might imply
-  % \end{itemize}
-% \end{frame}
-% \subsection{Basic matroid theory}
-% \begin{frame}
-  % \begin{itemize}
-  %   \item (2/3 slides)
-  %   \item Formally define matroids
-  %   \item Explain the meaning of the definition by using the example
-  %   \item Contraction and deletion (again with example)
-  %   \item Define Matroid games (and mention that the example fits)
-  % \end{itemize}
+  \frametitle{Operations on Matroids $\mathcal{M} = \tupel{E, \mathcal{B}}$}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{center}
+      Contraction:
+    \end{center}
+    \vspace{-0.6cm}
+    \begin{align*}
+      &\mathcal{M}/e = \tupel{E\setminus\set{e}, \mathcal{B}/e}\text{ with}\\
+      &\mathcal{B}/e = \set{B\subseteq (E\setminus\set{e})\middle| B\cup\set{e}\in\mathcal{B}}
+    \end{align*}
+    \column<4->{0.5\textwidth}
+    \begin{center}
+      Deletion:
+    \end{center}
+    \vspace{-0.6cm}
+    \begin{align*}
+      &\mathcal{M}\setminus e = \tupel{E\setminus\set{e},\mathcal{B}\setminus e}\text{ with}\\
+      &\mathcal{B}\setminus e = \set{B\subseteq E\setminus\set{e}\middle|B\in\mathcal{B}}
+    \end{align*}
+  \end{columns}
+  \begin{center}
+    \begin{tikzpicture}
+      \uncover<2->{\node (G) {\input{tikz/graphp1}};
+      \node[right=1 of G] (leadsto) {\Huge$\leadsto$};}
+      \uncover<3>{\node[right=1 of leadsto] (G') {\input{tikz/graphp1Cont}};}
+      \uncover<5>{\node[right=1 of leadsto] (G'') {\input{tikz/graphp1Del}};}
+    \end{tikzpicture}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Cuts in Matroids}
+  \begin{columns}
+    \column{0.7\textwidth}
+    $\mathcal{M} = \tupel{E, \mathcal{B}}$
+    \begin{itemize}
+      \item \emph{Cut}: inclusion-wise minimal $C\subseteq E$ such that
+        $E\setminus C$ does not contain a basis of $\mathcal{M}$
+      \item[$\leadsto$] $\mathcal{C}\tupel{\mathcal{M}} =
+        \set{C\subseteq E\middle| C\text{ is a cut in } \mathcal{M}}$
+    \end{itemize}
+    \column{0.3\textwidth}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}
+  \end{columns}
+  \vspace{0.7cm}
+  \begin{columns}
+    \column{0.33\textwidth}
+    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut1}}\\[0.3cm]}
+    \uncover<3->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut2}}}
+    \column{0.33\textwidth}
+    \uncover<4->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}\\[0.3cm]
+    \uncover<5->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut4}}}
+    \column{0.33\textwidth}
+    \uncover<6->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut5}}}
+  \end{columns}
 \end{frame}
@@
 \begin{frame}
-  % \begin{itemize}
-  %   \item Present algorithm (2 slides)
-  %   \item Execute one or two steps at example (only a slide but animation might
-  %     take some time ca. 5 minutes)
-  % \end{itemize}
+  \frametitle{Algorithm}
+  \begin{tabular}{|lll|}
+    \hline
+    (i) & Init: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item \parbox{0.7\textwidth}{every player: empty working basis, complete ground-set, complete set of valid result bases}
+          \item every resource: cost for next load, current load
+        \end{itemize}
+      }\\\hline
+    (ii) & Find: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item inclusion-min (necessary cost)-max cut $C$
+          \item minimal cost resource $e$ in $C$
+          \item owner $i$ of $C$
+        \end{itemize}
+      }\\\hline
+    (iii) & Pick: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item $i$: add $e$ to working basis, contract matroid to $e$
+          \item $e$: update marginal cost and increase load
+          \item all player: delete elements $C\setminus\set{e}$ from matroid
+        \end{itemize}
+      }\\\hline
+    (iv) & Break: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item exists player with incomplete basis: goto (ii)
+          \item otherwise: return chosen bases and payments
+        \end{itemize}
+      }\\\hline
+  \end{tabular}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Example: Graph}
+  \resizebox{\textwidth}{!}{\input{tikz/graphp2}}
 \end{frame}

### 2017-01-07 slides.tex
added example, added soundness intuition

@@
 \usepackage{csquotes}
+\usepackage{cancel}
 \usetheme{metropolis}
@@
 \begin{frame}
-  % \begin{itemize}
-  %   \item Context (1 slide)
-  %     \begin{itemize}
-  %       \item What is modelled?
-  %       \item How is it modelled?
-  %     \end{itemize}
-  %   \item Example (1 slide)
-  %     \begin{itemize}
-  %       \item Introducing an example which is used to illustrate different
-  %         aspects throughout the presentation
-  %       \item Interleaved graphs for two players, both want to acquire a
-  %         spanning tree
-  %     \end{itemize}
-  % \end{itemize}
 \end{frame}
@@
   \frametitle{Example: Graph}
-  \resizebox{\textwidth}{!}{\input{tikz/graphp2}}
+  \begin{columns}
+    \column{0.5\textwidth}
+    Player 1:\\
+    \vspace{-0.2cm}
+    \begin{center}
+      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp1labeled}}
+    \end{center}
+    \column{0.5\textwidth}
+    Player 2:\\
+    \vspace{-0.5cm}
+    \begin{center}
+      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp2labeled}}
+    \end{center}
+  \end{columns}
+  \begin{center}
+    \resizebox{0.35\textwidth}{!}{\input{tikz/graphboth}}
+  \end{center}
 \end{frame}
 
-\subsection{Correctness}
+\newlength{\cutscaling}
+\setlength{\cutscaling}{0.17\textwidth}
 \begin{frame}
-  % \begin{itemize}
-  %   \item Intuitively present the ideas for the correctness (1/2 slides)
-  %   \item (Formal proofs might take too long?)
-  % \end{itemize}
+  \frametitle{Example: Algorithm}
+  \begin{columns}
+    % left column:
+    \column{0.3\textwidth}
+    \resizebox{\textwidth}{!}{\alt<1-6>{\input{tikz/graphp1}}{\alt<7>{\input{tikz/graphp1Cont}}{\input{tikz/graphp1ContDel}}}}
+    \begin{columns}
+      \column{0.5\textwidth}
+      \resizebox{\cutscaling}{!}{\alt<1-2>{\input{tikz/graphp1Cut1}}{\input{tikz/graphp1Cut1value}}}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut2}}{\input{tikz/graphp1Cut2value}}}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut3}}{\input{tikz/graphp1Cut3value}}}
+      \column{0.5\textwidth}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut4}}{\input{tikz/graphp1Cut4value}}}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut5}}{\input{tikz/graphp1Cut5value}}}
+    \end{columns}
+
+    % middle column:
+    \column{0.4\textwidth}
+    \resizebox{\textwidth}{!}{\alt<1-8>{\input{tikz/graphbothCosts}}{\input{tikz/graphbothCostsUpd}}}
+    \begin{center}
+      \uncover<5->{\alt<5>{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3marked}}}}
+    \end{center}
+
+    % right column:
+    \column{0.3\textwidth}
+    \resizebox{\textwidth}{!}{\alt<1-7>{\input{tikz/graphp2}}{\input{tikz/graphp2Del}}}
+    \begin{columns}
+      \column{0.5\textwidth}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut1}}{\input{tikz/graphp2Cut1value}}}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut2}}{\input{tikz/graphp2Cut2value}}}
+      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut3}}{\input{tikz/graphp2Cut3deleted}}}
+      \column{0.5\textwidth}
+      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut4}}{\input{tikz/graphp2Cut4deleted}}}
+      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut5}}{\input{tikz/graphp2Cut5deleted}}}
+      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut6}}{\input{tikz/graphp2Cut6value}}}
+    \end{columns}
+  \end{columns}
+  \uncover<9>{ }
+\end{frame}
+
+\begin{frame}
+  \frametitle{Soundness}
+  \begin{itemize}
+    \item Termination:
+      \begin{itemize}
+        \item inductively applying contraction operations lead to basis
+        \item deletion cannot \enquote{loose} bases for other players since
+          chosen cut is inclusion-wise minimal
+      \end{itemize}
+    \item Correctness
+      \begin{itemize}
+        \item Lemma: cost of the chosen element decreases monotonically in each
+          iteration
+        \item assume there is a beneficial alternative basis
+          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
+          \begin{itemize}
+            \item consider iteration $k$ in which $g$ is added to basis of $i$:
+            \item if $f$ is in the corresonponding cut its cost never changes
+              since it is deleted from every matroid $rightarrow$ $f$ is not in
+              the cut
+            \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
+              is not left in contracted matroid of $i$
+            \item $f$ was deleted before (in this iteration the cost of the
+              chosen element was lower than for $f$ in contradiction to lemma)
+          \end{itemize}
+      \end{itemize}
+  \end{itemize}
 \end{frame}
@@
   %   \item Show (or at least motivate) why this is a PNE
-  %   \item Mention reduction to show that finding an optimal solution is NP-hard
+  %   \item Mention reduction to show that finding an optimal solution is
+  %     NP-hard
   % \end{itemize}

### 2017-01-07 tikz/graphbothCostsUpd.tex
added example, added soundness intuition

\begin{tikzpicture}
  \node[node] (A) {};
  \node[below=0.5 of A] (d1) {};
  \node[node, below=0.5 of d1] (B) {};
  \node[right=1 of A] (d2) {};
  \node[node, right=1 of d2] (D) {};
  \node[node] (C) at (d1-|d2) {};
  \node[node] (E) at (B-|D) {};
  \node[node, above=0.5 of d2] (F) {};

  \draw[edge, p1] (A) to node[right, black, label={[black,label distance=-0.2cm]right:\tiny$8$}] {\tiny\bcancel{$7$}} (B);
  \draw[edge, both, dotted] (A) to node[above, black] {\tiny$8$} (C);
  \draw[edge, p1] (B) to node[below, black] {\tiny$2$} (C);
  \draw[edge, both] (C) to node[above, black] {\tiny$3$} (D);
  \draw[edge, p1] (C) to node[below, black] {\tiny$6$} (E);
  \draw[edge, p2] (A) to node[above, black] {\tiny$5$} (F);
  \draw[edge, p2] (D) to node[above, black] {\tiny$2$} (F);
\end{tikzpicture}

### 2017-01-07 tikz/graphp1ContDel.tex
added example, added soundness intuition

--- 2017-01-07 tikz/graphbothCostsUpd.tex
@@
   \node[node] (E) at (B-|D) {};
-  \node[node, above=0.5 of d2] (F) {};
 
-  \draw[edge, p1] (A) to node[right, black, label={[black,label distance=-0.2cm]right:\tiny$8$}] {\tiny\bcancel{$7$}} (B);
-  \draw[edge, both, dotted] (A) to node[above, black] {\tiny$8$} (C);
-  \draw[edge, p1] (B) to node[below, black] {\tiny$2$} (C);
-  \draw[edge, both] (C) to node[above, black] {\tiny$3$} (D);
-  \draw[edge, p1] (C) to node[below, black] {\tiny$6$} (E);
-  \draw[edge, p2] (A) to node[above, black] {\tiny$5$} (F);
-  \draw[edge, p2] (D) to node[above, black] {\tiny$2$} (F);
+  \node[fit=(A) (B), draw, rectangle, rounded corners, black] (new) {};
+
+  \draw[edge, p1, bend right, dotted] (C) to (new.east);
+  \draw[edge, p1, bend left] (C) to (new.east);
+  \draw[edge, p1] (A) to (B);
+  \draw[edge, p1] (C) to (D);
+  \draw[edge, p1] (C) to (E);
 \end{tikzpicture}

### 2017-01-11 slides.tex
added lemma and theorem for non-matroid space

@@
 \newcommand{\set}[1]{\left\{#1\right\}}
+
+\DeclareMathOperator{\ex}{ex}
 
@@
             \item if $f$ is in the corresonponding cut its cost never changes
-              since it is deleted from every matroid $rightarrow$ $f$ is not in
-              the cut
+              since it is deleted from every matroid $\rightarrow$ $f$ is not
+              in the cut
             \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
@@
 \begin{frame}
-  % \begin{itemize}
-  %   \item (2 slides)
-  %   \item Introduce socially optimal solution
-  %   \item Show (or at least motivate) why this is a PNE
-  %   \item Mention reduction to show that finding an optimal solution is
-  %     NP-hard
-  % \end{itemize}
+  \frametitle{Recall: Congestion Model}
+  \begin{equation*}
+    \mathcal{M} = \tupel{N, E, \mathcal{B}, \left(d_{i}\right)_{i\in N},
+    \left(c_{e}\right)_{e\in E}}
+  \end{equation*}
+  \vspace{-1cm}
+  \begin{itemize}
+    \item before: $d_{i} = 1$ for all $i$
+    \item now: $d_{i}\in\mathbb{N}_{>0}$ 
+    \item auxiliary definitions:
+      \begin{itemize}
+        \item $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
+        \item for a fixed $B$: $\ex_{i}\tupel{e} =
+          \set{f\in E\setminus\set{e}\middle|
+          (B_{i}\setminus{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
+          that can replace $e$ for player $i$
+        \item $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
+          set of obligatory elements for at least one player
+        \item $\Delta_{i}\tupel{B;e\rightarrow f} =
+          c_{f}\tupel{\ell_{f}\tupel{B_{i}\cup\set{f}\setminus\set{e}}} -
+          c_{f}\tupel{\ell_{f}\tupel{B}}$: marginal cost to buy resource $f$ if
+          $i$ switches
+        \item $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
+          minimal marginal cost for exchanging $e$
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Characterisation of Pure Nash Equilibria}
+  \begin{theorem}
+    For a weighted matroid resource buying game
+    $\tupel{N, E, \mathcal{B}, d, c}$ and $B\in\mathcal{B}$ the following
+    holds: there is a payment vector $p$ such that $\tupel{B,p}$ is a
+    PNE if and only if
+    \begin{equation*}
+      c_{e}(B) \leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
+      \textit{ for all }e\in E\setminus F
+    \end{equation*}
+  \end{theorem}
+  \begin{proof}
+    if: $p_{i}^{e} =
+      \begin{cases}
+        \frac{\Delta_{i}^{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}\cdot
+        c_{e}(B)&\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) > 0\\
+        0 &\text{ otherwise}
+      \end{cases}$\\
+      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\
+    only if: for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
+      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$
+  \end{proof}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Existence of Pure Nash Equilibria}
+  \begin{theorem}
+    Every weighted matroid resource buying game with marginally non-increasing
+    cost functions possesses a pure Nash equilibria.
+  \end{theorem}
+  \begin{itemize}
+    \item socially optimal configuration profile: $B\in\mathcal{B}$ such that
+      $\sum_{e\in E}c_{e}(\ell_{e}(B))$ is minimal
+    \item for socially optimal configuration profile $B$ holds:
+      \begin{equation*}
+        c_{e}(B)\leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
+        \text{ for all }e\in E\setminus F
+      \end{equation*}
+    \item $B$ is a pure Nash equilibrium
+    \item (but finding socially optimal configuration profiles is NP-hard)
+  \end{itemize}
 \end{frame}
@@
 \section{Non-Matroid Strategy Spaces}
-\subsection{Lack of PNE}
 \begin{frame}
-  % \begin{itemize}
-  %   \item (1 slide)
-  %   \item Present that for Non-Matroid Games we can find strategy spaces
-  %     which do not allow PNE
-  %   \item Illustrate the construction by a picture
-  % \end{itemize}
+\frametitle{Consequences of using Non-Matroid Strategy Spaces}
+  \begin{lemma}
+    If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there
+    exist $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
+    set $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains
+    $b$ and $c$. (Especially, there is $S\in\mathcal{S}$ with
+    $S\subseteq X\cup Y$ and $a\in S$ but $b,c\notin S$.)
+  \end{lemma}
+  \begin{theorem}
+    For every non-matroid anti-chain $\mathcal{S}$ on a set of resource $E$,
+    there exists a weighted two-player resource buying game
+    $G = \tupel{\tilde{E}, \tupel{\mathcal{S}_{1} \times
+    \mathcal{S}_{2}}\times \mathcal{P}, \pi}$ having marginally non-increasing
+    cost functions, whose strategy spaces $\mathcal{S}_{1}$ and
+    $\mathcal{S}_{2}$ are both isomophic to $\mathcal{S}$, so that $G$ does not
+    possess a pure Nash equilibrium.
+  \end{theorem}
 \end{frame}
 
-\subsection{Non-Decreasing Marginal Cost Functions \& Price of Anarchy}
 \begin{frame}
-  % \begin{itemize}
-  %   \item (3 slides)
-  %   \item Present that games with Non-Decreasing Marginal Cost Functions allow
-  %     PNE (explain how the marginal cost pricing is obtained)
-  %   \item Define Price of Anarchy
-  %   \item Mention that non-increasing and non-decreasing games with weighted
-  %     players is unbounded
-  % \end{itemize}
+  \frametitle{Construction of games without PNE}
+
 \end{frame}
@@
 \begin{frame}
-  % \begin{itemize}
-  %   \item (1 slide)
-  %   \item Sum up results
-  %   \item Embed results into topic
-  % \end{itemize}
 \end{frame}

### 2017-02-01 slides.tex
added explaining picture to construct game without pne
work work work
added theorem and explanation on non-decreasing marginal cost functions, decided to leave anarchy out since the explanation is rather dubious

@@
 \usepackage{cancel}
+\usepackage{stmaryrd}
 \usetheme{metropolis}
@@
 \maketitle
-\section{Introduction}
+
 \begin{frame}
+  \frametitle{Introduction}
 \end{frame}
 
-\subsection{Game definition}
+\section{Basic Definitions}
 \begin{frame}
@@
     \begin{align*}
-      &\mathcal{M}\setminus e = \tupel{E\setminus\set{e},\mathcal{B}\setminus e}\text{ with}\\
+      &\mathcal{M}\setminus e = \tupel{E\setminus\set{e},\mathcal{B}\setminus \set{e}}\text{ with}\\
       &\mathcal{B}\setminus e = \set{B\subseteq E\setminus\set{e}\middle|B\in\mathcal{B}}
@@
     Every weighted matroid resource buying game with marginally non-increasing
-    cost functions possesses a pure Nash equilibria.
+    cost functions possesses a PNE.
   \end{theorem}
@@
       \end{equation*}
-    \item $B$ is a pure Nash equilibrium
+    \item for $B$ exists $p$ s.t. $\tupel{B,p}$ is a PNE
     \item (but finding socially optimal configuration profiles is NP-hard)
@@
   \frametitle{Construction of games without PNE}
+   \begin{columns}
+     \column{0.3\textwidth}
+       \begin{itemize}
+         \item $c_{x}(t) = t$
+         \item $c_{y}(t) = 5\frac{1}{2}$
+         \item $c_{z}(t) = 4$
+         \item $d_{1} = 5$
+         \item $d_{2} = 4$
+       \end{itemize}
+     \column{0.7\textwidth}
+       \begin{center}
+         \resizebox{\textwidth}{!}{\input{tikz/gamediagram}}
+       \end{center}
+   \end{columns}
+   \begin{itemize}
+     \item assume PNE $\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
+       p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$
+     \item $Z_{i}^{\ast}\subseteq\tupel{X_{i}\cup Y_{i}}$
+     \item $x\not\in Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast}$
+     \item $y\not\in Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}$
+     \item[$\Rightarrow$] neiter $x\in Z_{1}^{\ast}$ nor $x\not\in Z_{1}^{\ast}$ $\lightning$
+   \end{itemize}
+\end{frame}
 
+\begin{frame}
+  \frametitle{Non-Decreasing Marginal Cost Functions}
+  \begin{columns}
+    \column{0.5\textwidth}
+      Non-Increasing Marginal Cost Functions:
+      \begin{center}
+        \begin{tikzpicture}
+          \begin{axis}[
+              xlabel=$x$,
+              ylabel=$c_{e}(x)$,
+              smooth,
+              width=5cm,
+              height=3cm,
+              ticks=none,
+              no markers
+            ]
+              \addplot{ln(x)};
+          \end{axis}
+        \end{tikzpicture}
+      \end{center}
+    \column{0.5\textwidth}
+      Non-Decreasing Marginal Cost Functions:
+      \begin{center}
+        \begin{tikzpicture}
+          \begin{axis}[
+              xlabel=$x$,
+              xmin=1,
+              xmax=4,
+              ylabel=$c_{e}(x)$,
+              smooth,
+              width=5cm,
+              height=3cm,
+              ticks=none,
+              no markers
+            ]
+              \addplot{5*exp(x)};
+          \end{axis}
+        \end{tikzpicture}
+      \end{center}
+  \end{columns}
+  \begin{theorem}
+    Let $G$ be a weighted resource buying game with non-decreasing marginal
+    costs and let $S^{\ast}$ be a socially optimal solution. We can compute
+    (so called) marginal cost pricing vectors which induce a PNE.
+  \end{theorem}
 \end{frame}

### 2017-02-01 slides.tex
finished conclusion and introduction

@@
 \usepackage{stmaryrd}
+\usepackage{url}
 \usetheme{metropolis}
@@
   \frametitle{Introduction}
+    \begin{itemize}
+      \item Resources: Nodes/edges in a graph, Machines to schedule jobs on,
+        \dots
+      \item Players: jointly buy resources to meet individual
+        (potentially overlapping) demands
+      \item<2-> Every player contributes to buy certain resources
+      \item<3-> Payoff for a player depends on what she payed to meet her demands
+        of resources
+    \end{itemize}
+    \uncover<4->{\begin{definition}[Pure Nash Equilibrium(informal)]
+      A \emph{Pure Nash Equilibrium (PNE)} is given if for every player holds
+      that, given all other players stick to their strategies, she cannot alter
+      her behaviour to achieve a better payoff for herself.
+    \end{definition}}
 \end{frame}
@@
     \item $N$: set of players
-    \item $E$: set of resources
-    \item $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
+    \item<2-> $E$: set of resources
+    \item<3-> $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
       set of desired resources $S_{i}\subseteq E$: set of configurations
-    \item $d_{i}$: demand of player $i$ for her resource
+    \item<4-> $d_{i}$: demand of player $i$ for her resource
       \begin{itemize}
-        \item $d_{i} = 1$ for an unweighted game
-        \item $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
+        \item<4-> $d_{i} = 1$ for an unweighted game
+        \item<4-> $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
           in configuration $S\in\mathcal{S}$
       \end{itemize}
-    \item $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
+    \item<5-> $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
       $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
@@
   \begin{itemize}
-    \item $\mathcal{P}=\times_{i\in N} P_{i}$ with
+    \item<2-> $\mathcal{P}=\times_{i\in N} P_{i}$ with
       $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
-    \item $e\in E$ is bought under $S\in \mathcal{S}$ if
+    \item<3-> $e\in E$ is bought under $S\in \mathcal{S}$ if
       $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
-    \item $\pi_{i}(S) =
+    \item<4-> $\pi_{i}(S) =
       \begin{cases}
@@
     \item \emph{unweighted} games
-    \item marginally non-increasing cost-function $c_{e}$:
+    \item<2-> marginally non-increasing cost-function $c_{e}$:
       \begin{equation*}
@@
       \end{center}
-    \item restrict players demands to a specific mathematical structure:
+    \item<3-> restrict players demands to a specific mathematical structure:
       Matroids
@@
 \begin{frame}
+  \frametitle{Cuts in Matroids}
+  \begin{columns}
+    \column{0.7\textwidth}
+    $\mathcal{M} = \tupel{E, \mathcal{B}}$
+    \begin{itemize}
+      \item \emph{Cut}: inclusion-wise minimal $C\subseteq E$ such that
+        $E\setminus C$ does not contain a basis of $\mathcal{M}$
+      \item[$\leadsto$] $\mathcal{C}\tupel{\mathcal{M}} =
+        \set{C\subseteq E\middle| C\text{ is a cut in } \mathcal{M}}$
+    \end{itemize}
+    \column{0.3\textwidth}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}
+  \end{columns}
+  \vspace{0.7cm}
+  \begin{columns}
+    \column{0.33\textwidth}
+    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut1}}\\[0.3cm]}
+    \uncover<3->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut2}}}
+    \column{0.33\textwidth}
+    \uncover<4->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}\\[0.3cm]
+    \uncover<5->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut4}}}
+    \column{0.33\textwidth}
+    \uncover<6->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut5}}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
   \frametitle{Operations on Matroids $\mathcal{M} = \tupel{E, \mathcal{B}}$}
@@
   \end{center}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Cuts in Matroids}
-  \begin{columns}
-    \column{0.7\textwidth}
-    $\mathcal{M} = \tupel{E, \mathcal{B}}$
-    \begin{itemize}
-      \item \emph{Cut}: inclusion-wise minimal $C\subseteq E$ such that
-        $E\setminus C$ does not contain a basis of $\mathcal{M}$
-      \item[$\leadsto$] $\mathcal{C}\tupel{\mathcal{M}} =
-        \set{C\subseteq E\middle| C\text{ is a cut in } \mathcal{M}}$
-    \end{itemize}
-    \column{0.3\textwidth}
-    \resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}
-  \end{columns}
-  \vspace{0.7cm}
-  \begin{columns}
-    \column{0.33\textwidth}
-    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut1}}\\[0.3cm]}
-    \uncover<3->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut2}}}
-    \column{0.33\textwidth}
-    \uncover<4->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}\\[0.3cm]
-    \uncover<5->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut4}}}
-    \column{0.33\textwidth}
-    \uncover<6->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut5}}}
-  \end{columns}
 \end{frame}
@@
       \begin{itemize}
-        \item inductively applying contraction operations lead to basis
-        \item deletion cannot \enquote{loose} bases for other players since
+        \item<2-> inductively applying contraction operations lead to basis
+        \item<3-> deletion cannot \enquote{loose} bases for other players since
           chosen cut is inclusion-wise minimal
@@
       \begin{itemize}
-        \item Lemma: cost of the chosen element decreases monotonically in each
+        \item<4-> Lemma: cost of the chosen element decreases monotonically in each
           iteration
-        \item assume there is a beneficial alternative basis
+        \item<5-> assume there is a beneficial alternative basis
           $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
           \begin{itemize}
-            \item consider iteration $k$ in which $g$ is added to basis of $i$:
-            \item if $f$ is in the corresonponding cut its cost never changes
+            \item<6-> consider iteration $k$ in which $g$ is added to basis of $i$:
+            \item<7-> if $f$ is in the corresonponding cut its cost never changes
               since it is deleted from every matroid $\rightarrow$ $f$ is not
               in the cut
-            \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
+            \item<8-> but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
               is not left in contracted matroid of $i$
-            \item $f$ was deleted before (in this iteration the cost of the
+            \item<9-> $f$ was deleted before (in this iteration the cost of the
               chosen element was lower than for $f$ in contradiction to lemma)
@@
     \item before: $d_{i} = 1$ for all $i$
-    \item now: $d_{i}\in\mathbb{N}_{>0}$ 
-    \item auxiliary definitions:
+    \item<2-> now: $d_{i}\in\mathbb{N}_{>0}$ 
+    \item<3-> auxiliary definitions:
       \begin{itemize}
-        \item $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
-        \item for a fixed $B$: $\ex_{i}\tupel{e} =
+        \item<4-> $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
+        \item<5-> for a fixed $B$: $\ex_{i}\tupel{e} =
           \set{f\in E\setminus\set{e}\middle|
@@
           that can replace $e$ for player $i$
-        \item $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
+        \item<6-> $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
           set of obligatory elements for at least one player
-        \item $\Delta_{i}\tupel{B;e\rightarrow f} =
+        \item<7-> $\Delta_{i}\tupel{B;e\rightarrow f} =
           c_{f}\tupel{\ell_{f}\tupel{B_{i}\cup\set{f}\setminus\set{e}}} -
@@
           $i$ switches
-        \item $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
+        \item<8-> $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
           minimal marginal cost for exchanging $e$
@@
   \begin{proof}
-    if: $p_{i}^{e} =
+    if: \uncover<2->{$p_{i}^{e} =
       \begin{cases}
@@
       \end{cases}$\\
-      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\
-    only if: for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
-      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$
+      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\}
+    only if: \uncover<3->{for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
+      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$}
   \end{proof}
@@
   \begin{itemize}
-    \item socially optimal configuration profile: $B\in\mathcal{B}$ such that
+    \item<2-> socially optimal configuration profile: $B\in\mathcal{B}$ such that
       $\sum_{e\in E}c_{e}(\ell_{e}(B))$ is minimal
-    \item for socially optimal configuration profile $B$ holds:
+    \item<3-> for socially optimal configuration profile $B$ holds:
       \begin{equation*}
@@
       \end{equation*}
-    \item for $B$ exists $p$ s.t. $\tupel{B,p}$ is a PNE
-    \item (but finding socially optimal configuration profiles is NP-hard)
+    \item<4-> for $B$ exists $p$ s.t. $\tupel{B,p}$ is a PNE
+    \item<5-> (but finding socially optimal configuration profiles is NP-hard)
   \end{itemize}
@@
   \end{lemma}
-  \begin{theorem}
+  \uncover<2->{\begin{theorem}
     For every non-matroid anti-chain $\mathcal{S}$ on a set of resource $E$,
@@
     possess a pure Nash equilibrium.
-  \end{theorem}
+  \end{theorem}}
 \end{frame}
@@
    \begin{itemize}
-     \item assume PNE $\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
+     \item<2-> assume PNE $\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
        p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$
-     \item $Z_{i}^{\ast}\subseteq\tupel{X_{i}\cup Y_{i}}$
-     \item $x\not\in Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast}$
-     \item $y\not\in Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}$
-     \item[$\Rightarrow$] neiter $x\in Z_{1}^{\ast}$ nor $x\not\in Z_{1}^{\ast}$ $\lightning$
+     \item<3-> $Z_{i}^{\ast}\subseteq\tupel{X_{i}\cup Y_{i}}$
+     \item<4-> $x\not\in Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast}$
+     \item<5-> $y\not\in Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}$
+     \item<6->[$\Rightarrow$] neiter $x\in Z_{1}^{\ast}$ nor $x\not\in Z_{1}^{\ast}$ $\lightning$
    \end{itemize}
@@
   \end{columns}
-  \begin{theorem}
+  \uncover<2->{\begin{theorem}
     Let $G$ be a weighted resource buying game with non-decreasing marginal
@@
     (so called) marginal cost pricing vectors which induce a PNE.
-  \end{theorem}
+  \end{theorem}}
 \end{frame}
@@
 \begin{frame}
+  \frametitle{Results}
+  \begin{itemize}
+    \item Resource Buying Games
+    \item<2-> Matroids:
+      \parbox{6cm}{
+        \begin{itemize}
+          \item Operations: Contraction, Deletion
+          \item Cuts
+        \end{itemize}
+      }
+    \item<3-> Games:
+      \parbox{8cm}{
+        \begin{itemize}
+          \item \parbox{6cm}{
+              \begin{tabular}{|l|ll|}
+                \hline
+                Non-increasing marginal & Matroid & No Matroid\\\hline
+                unweighted & Algorithm & \\
+                weighted & PNE & No PNE\\\hline
+                Non-decreasing marginal & PNE & \\\hline
+              \end{tabular}
+            }
+        \end{itemize}
+      }
+    \item<4-> Slides: \url{github.com/weltoph/sem-alg-gametheory}
+  \end{itemize}
+  \uncover<5->{\centering Thank you for your attention!}
 \end{frame}

### 2017-02-21 paper.tex
started work on paper

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage[framed]{ntheorem}

\theoremstyle{nonumberplain}
\newframedtheorem{defi}{Definition}
\newframedtheorem{theo}{Theorem}

\title{Resource Buying Games}
\author{Christoph Welzel}

\begin{document}
\maketitle

\begin{defi}[Marginally non-increasing]
  Whoop
\end{defi}

\end{document}

### 2017-02-24 paper.tex
matroids in paper write up

@@
 \usepackage{framed}
+\usepackage{todo}
 \usepackage[framed]{ntheorem}
@@
 
+\newcommand{\tupel}[1]{\left(#1\right)}
+\newcommand{\set}[1]{\left\{#1\right\}}
+
 \title{Resource Buying Games}
@@
 \begin{document}
+\input{tikz/settings}
 \maketitle
+\section{Introduction}
 
-\begin{defi}[Marginally non-increasing]
-  Whoop
+\section{Matroids}
+In this section we present the combinatorial structure of Matroids.
+\todo{why matroids?}
+
+We use matroids as a generalisation of the concept of linear independence.
+Matroids can be defined as a ground-set and the family of linear
+independent sets of this ground-set. This family has to satisfy three
+properties, i.e.
+\begin{enumerate}
+  \item the empty set is linear independent,
+  \item all subset of a linear independent set are linear independent and
+  \item for two linear independent sets we can find an element of the larger
+    set that forms a linear independent set when added to the smaller set.
+\end{enumerate}
+We use an equivalent definition of matroids which in a way captures the idea of
+having a vector space by giving instead of linear independent sets the bases of
+the ground-set.
+\begin{defi}
+  The structure $\tupel{E, \mathcal{B}}$ with $\mathcal{B}\subseteq 2^{E}$ is
+  a matroid if
+  \begin{enumerate}
+    \item $\mathcal{B}\neq\emptyset$
+    \item let $B,B'\in\mathcal{B}$ and for every $x\in B$ there is $y\in B'$
+      s. t. $(B\setminus\set{x})\cup\set{y}\in\mathcal{B}$
+  \end{enumerate}
 \end{defi}
+In analogy to vector spaces we consider every element of a basis to open access
+to a dimension. We illustrate this concept with the following example: given an
+undirected connected graph $G = \tupel{V, E}$ we will argue that
+$\tupel{E, \mathcal{S}}$ with $\mathcal{S}$ as edge-sets of spanning trees
+in $G$ forms a matroid. In order to meet the requirement that $\mathcal{S}$
+must not be empty we restrict $G$ to those graphs with at least two distinct
+vertices. Furthermore, given two spanning trees $\tupel{V, S_{1}}$ and
+$\tupel{V, S_{2}}$ of $G$ then removing an edge from $S_{1}$ yields a subgraph
+of $G$ that is separated into two connected components. Since $S_{2}$ forms a
+spanning tree as well there must be an edge connecting these components which
+can be used to again obtain a spanning tree\footnote{see Figure
+\ref{fig:spanning} for an illustration}. Consider the algorithm of Prim
+which computes spanning trees by iteratively adding edges which do not close a
+cycle: every added edge works towards a basis in $\mathcal{S}$ and opens a
+dimensionality by connecting one of the graph nodes.
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (t) {\input{tikz/graphp1}};
+      \node[below left=of t] {\input{tikz/graphp1S1}};
+      \node[below =of t] {\input{tikz/graphp1S2}};
+      \node[below right=of t] {\input{tikz/graphp1S1}};
+    \end{tikzpicture}
+  \end{center}
+  \caption{Graph with its spanning trees}
+  \label{fig:spanning}
+\end{figure}
+\todo{working iteratively towards a basis by prim's algorithm as example to
+introduce cuts and contractions and deletions}
+
+\todos
 

### 2017-02-28 alg.tex
proceeded on paper, added algorithm on separated pdf for transparency print

--- 2017-01-11 slides.tex
@@
-\documentclass{beamer}
-\usepackage{pgfplots}
-\usepackage{tikz}
-\usepackage{csquotes}
-\usepackage{cancel}
-\usetheme{metropolis}
-\title{Resource Buying Games}
-\author[C. Welzel]{Christoph Welzel}
-
+\documentclass{scrartcl}
 \newcommand{\tupel}[1]{\left(#1\right)}
 \newcommand{\set}[1]{\left\{#1\right\}}
-
-\DeclareMathOperator{\ex}{ex}
-
 \begin{document}
-\input{tikz/settings}
-\maketitle
-\section{Introduction}
-\begin{frame}
-\end{frame}
-
-\subsection{Game definition}
-\begin{frame}
-  \frametitle{Definition: congestion model}
-  \begin{equation*}
-    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
-    \left(c_{e}\right)_{e\in E}}
-  \end{equation*}
-  \vspace{-1cm}
-  \begin{itemize}
-    \item $N$: set of players
-    \item $E$: set of resources
-    \item $\mathcal{S} = \times_{i\in N}\mathcal{S}_{i}$ with $\mathcal{S}_{i}$
-      set of desired resources $S_{i}\subseteq E$: set of configurations
-    \item $d_{i}$: demand of player $i$ for her resource
-      \begin{itemize}
-        \item $d_{i} = 1$ for an unweighted game
-        \item $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$: load of $e$
-          in configuration $S\in\mathcal{S}$
-      \end{itemize}
-    \item $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
-      $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
-      of $S$
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Definition: weighted resource buying game}
-  \begin{equation*}
-    \mathcal{M} = \tupel{N, E, \mathcal{S}, \left(d_{i}\right)_{i\in N},
-    \left(c_{e}\right)_{e\in E}}
-  \end{equation*}
-  \begin{equation*}
-    \leadsto\mathcal{G} = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
-  \end{equation*}
-  \vspace{-1cm}
-  \begin{itemize}
-    \item $\mathcal{P}=\times_{i\in N} P_{i}$ with
-      $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
-    \item $e\in E$ is bought under $S\in \mathcal{S}$ if
-      $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
-    \item $\pi_{i}(S) =
-      \begin{cases}
-        \sum_{e\in E}p_{i}^{e} &\textit{if }S_{i}\textit{ is bought}\\
-        \infty &\textit{otherwise}
-      \end{cases}$: {private cost of player $i$}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{A few simplifications}
-  \begin{itemize}
-    \item \emph{unweighted} games
-    \item marginally non-increasing cost-function $c_{e}$:
-      \begin{equation*}
-        c_{e}(x + \delta) - c_{e}(x) \geq c_{e}(y + \delta) - c_{e}(y)
-        \;\;x\leq y, \delta \in \mathbb{N}
-      \end{equation*}
-      \begin{center}
-        \begin{tikzpicture}
-          \begin{axis}[
-              xlabel=$x$,
-              ylabel=$c_{e}(x)$,
-              smooth,
-              width=5cm,
-              height=3cm,
-              ticks=none,
-              no markers
-            ]
-              \addplot{ln(x)};
-          \end{axis}
-        \end{tikzpicture}
-      \end{center}
-    \item restrict players demands to a specific mathematical structure:
-      Matroids
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Definition: Matroid}
-  \begin{columns}
-    \column{0.5\textwidth}
-    \begin{equation*}
-      M = (E, B)
-    \end{equation*}
-    \vspace{-0.8cm}
-    \begin{itemize}
-      \item $E$: ground-set
-      \item $B$: set of bases
-      \item \emph{basis exchange property}:
-        \vspace{-1cm}
-        \begin{center}
-          \begin{align*}
-            \forall &X, Y\in B:\\
-            &\forall x\in (X\setminus Y)\\
-            &\exists y\in (Y\setminus X):\\
-            &\;(X\setminus \set{x})\cup\{y\}\in B
-          \end{align*}
-        \end{center}
-    \end{itemize}
-    \column{0.5\textwidth}
-    \uncover<2->{Spanning trees:}
-    \begin{center}
-      \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}\\[0.5cm]}
-      \uncover<3->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S1}}}
-      \uncover<4->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S2}}}
-      \uncover<5->{\resizebox{0.4\textwidth}{!}{\input{tikz/graphp1S3}}}
-    \end{center}
-  \end{columns}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Operations on Matroids $\mathcal{M} = \tupel{E, \mathcal{B}}$}
-  \begin{columns}
-    \column{0.5\textwidth}
-    \begin{center}
-      Contraction:
-    \end{center}
-    \vspace{-0.6cm}
-    \begin{align*}
-      &\mathcal{M}/e = \tupel{E\setminus\set{e}, \mathcal{B}/e}\text{ with}\\
-      &\mathcal{B}/e = \set{B\subseteq (E\setminus\set{e})\middle| B\cup\set{e}\in\mathcal{B}}
-    \end{align*}
-    \column<4->{0.5\textwidth}
-    \begin{center}
-      Deletion:
-    \end{center}
-    \vspace{-0.6cm}
-    \begin{align*}
-      &\mathcal{M}\setminus e = \tupel{E\setminus\set{e},\mathcal{B}\setminus e}\text{ with}\\
-      &\mathcal{B}\setminus e = \set{B\subseteq E\setminus\set{e}\middle|B\in\mathcal{B}}
-    \end{align*}
-  \end{columns}
-  \begin{center}
-    \begin{tikzpicture}
-      \uncover<2->{\node (G) {\input{tikz/graphp1}};
-      \node[right=1 of G] (leadsto) {\Huge$\leadsto$};}
-      \uncover<3>{\node[right=1 of leadsto] (G') {\input{tikz/graphp1Cont}};}
-      \uncover<5>{\node[right=1 of leadsto] (G'') {\input{tikz/graphp1Del}};}
-    \end{tikzpicture}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Cuts in Matroids}
-  \begin{columns}
-    \column{0.7\textwidth}
-    $\mathcal{M} = \tupel{E, \mathcal{B}}$
-    \begin{itemize}
-      \item \emph{Cut}: inclusion-wise minimal $C\subseteq E$ such that
-        $E\setminus C$ does not contain a basis of $\mathcal{M}$
-      \item[$\leadsto$] $\mathcal{C}\tupel{\mathcal{M}} =
-        \set{C\subseteq E\middle| C\text{ is a cut in } \mathcal{M}}$
-    \end{itemize}
-    \column{0.3\textwidth}
-    \resizebox{0.8\textwidth}{!}{\input{tikz/graphp1}}
-  \end{columns}
-  \vspace{0.7cm}
-  \begin{columns}
-    \column{0.33\textwidth}
-    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut1}}\\[0.3cm]}
-    \uncover<3->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut2}}}
-    \column{0.33\textwidth}
-    \uncover<4->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}\\[0.3cm]
-    \uncover<5->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut4}}}
-    \column{0.33\textwidth}
-    \uncover<6->{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut5}}}
-  \end{columns}
-\end{frame}
-
-\section{Algorithm: PNE in Unweighted Matroid Games}
-\subsection{Algorithm}
-\begin{frame}
-  \frametitle{Algorithm}
   \begin{tabular}{|lll|}
@@
         \begin{itemize}
-          \item \parbox{0.7\textwidth}{every player: empty working basis, complete ground-set, complete set of valid result bases}
+          \item \parbox{0.7\textwidth}{every player: empty working basis,
+            complete ground-set, complete set of valid result bases}
           \item every resource: cost for next load, current load
@@
   \end{tabular}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Example: Graph}
-  \begin{columns}
-    \column{0.5\textwidth}
-    Player 1:\\
-    \vspace{-0.2cm}
-    \begin{center}
-      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp1labeled}}
-    \end{center}
-    \column{0.5\textwidth}
-    Player 2:\\
-    \vspace{-0.5cm}
-    \begin{center}
-      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp2labeled}}
-    \end{center}
-  \end{columns}
-  \begin{center}
-    \resizebox{0.35\textwidth}{!}{\input{tikz/graphboth}}
-  \end{center}
-\end{frame}
-
-\newlength{\cutscaling}
-\setlength{\cutscaling}{0.17\textwidth}
-\begin{frame}
-  \frametitle{Example: Algorithm}
-  \begin{columns}
-    % left column:
-    \column{0.3\textwidth}
-    \resizebox{\textwidth}{!}{\alt<1-6>{\input{tikz/graphp1}}{\alt<7>{\input{tikz/graphp1Cont}}{\input{tikz/graphp1ContDel}}}}
-    \begin{columns}
-      \column{0.5\textwidth}
-      \resizebox{\cutscaling}{!}{\alt<1-2>{\input{tikz/graphp1Cut1}}{\input{tikz/graphp1Cut1value}}}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut2}}{\input{tikz/graphp1Cut2value}}}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut3}}{\input{tikz/graphp1Cut3value}}}
-      \column{0.5\textwidth}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut4}}{\input{tikz/graphp1Cut4value}}}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut5}}{\input{tikz/graphp1Cut5value}}}
-    \end{columns}
-
-    % middle column:
-    \column{0.4\textwidth}
-    \resizebox{\textwidth}{!}{\alt<1-8>{\input{tikz/graphbothCosts}}{\input{tikz/graphbothCostsUpd}}}
-    \begin{center}
-      \uncover<5->{\alt<5>{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3marked}}}}
-    \end{center}
-
-    % right column:
-    \column{0.3\textwidth}
-    \resizebox{\textwidth}{!}{\alt<1-7>{\input{tikz/graphp2}}{\input{tikz/graphp2Del}}}
-    \begin{columns}
-      \column{0.5\textwidth}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut1}}{\input{tikz/graphp2Cut1value}}}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut2}}{\input{tikz/graphp2Cut2value}}}
-      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut3}}{\input{tikz/graphp2Cut3deleted}}}
-      \column{0.5\textwidth}
-      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut4}}{\input{tikz/graphp2Cut4deleted}}}
-      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut5}}{\input{tikz/graphp2Cut5deleted}}}
-      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut6}}{\input{tikz/graphp2Cut6value}}}
-    \end{columns}
-  \end{columns}
-  \uncover<9>{ }
-\end{frame}
-
-\begin{frame}
-  \frametitle{Soundness}
-  \begin{itemize}
-    \item Termination:
-      \begin{itemize}
-        \item inductively applying contraction operations lead to basis
-        \item deletion cannot \enquote{loose} bases for other players since
-          chosen cut is inclusion-wise minimal
-      \end{itemize}
-    \item Correctness
-      \begin{itemize}
-        \item Lemma: cost of the chosen element decreases monotonically in each
-          iteration
-        \item assume there is a beneficial alternative basis
-          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
-          \begin{itemize}
-            \item consider iteration $k$ in which $g$ is added to basis of $i$:
-            \item if $f$ is in the corresonponding cut its cost never changes
-              since it is deleted from every matroid $\rightarrow$ $f$ is not
-              in the cut
-            \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
-              is not left in contracted matroid of $i$
-            \item $f$ was deleted before (in this iteration the cost of the
-              chosen element was lower than for $f$ in contradiction to lemma)
-          \end{itemize}
-      \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\section{Weighted Matroid Games}
-\begin{frame}
-  \frametitle{Recall: Congestion Model}
-  \begin{equation*}
-    \mathcal{M} = \tupel{N, E, \mathcal{B}, \left(d_{i}\right)_{i\in N},
-    \left(c_{e}\right)_{e\in E}}
-  \end{equation*}
-  \vspace{-1cm}
-  \begin{itemize}
-    \item before: $d_{i} = 1$ for all $i$
-    \item now: $d_{i}\in\mathbb{N}_{>0}$ 
-    \item auxiliary definitions:
-      \begin{itemize}
-        \item $N_{e}\tupel{B} = \set{i\in N\middle|e\in B_{i}}$
-        \item for a fixed $B$: $\ex_{i}\tupel{e} =
-          \set{f\in E\setminus\set{e}\middle|
-          (B_{i}\setminus{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
-          that can replace $e$ for player $i$
-        \item $F = \bigcup_{i\in N}\bigcap_{B\in \mathcal{B}_{i}} B$:
-          set of obligatory elements for at least one player
-        \item $\Delta_{i}\tupel{B;e\rightarrow f} =
-          c_{f}\tupel{\ell_{f}\tupel{B_{i}\cup\set{f}\setminus\set{e}}} -
-          c_{f}\tupel{\ell_{f}\tupel{B}}$: marginal cost to buy resource $f$ if
-          $i$ switches
-        \item $\Delta_{i}^{e} = \min_{f\in\ex_{i}(e)}\set{\Delta_{i}(B;e\rightarrow f)}$:
-          minimal marginal cost for exchanging $e$
-      \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Characterisation of Pure Nash Equilibria}
-  \begin{theorem}
-    For a weighted matroid resource buying game
-    $\tupel{N, E, \mathcal{B}, d, c}$ and $B\in\mathcal{B}$ the following
-    holds: there is a payment vector $p$ such that $\tupel{B,p}$ is a
-    PNE if and only if
-    \begin{equation*}
-      c_{e}(B) \leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
-      \textit{ for all }e\in E\setminus F
-    \end{equation*}
-  \end{theorem}
-  \begin{proof}
-    if: $p_{i}^{e} =
-      \begin{cases}
-        \frac{\Delta_{i}^{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}\cdot
-        c_{e}(B)&\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) > 0\\
-        0 &\text{ otherwise}
-      \end{cases}$\\
-      for all $e\in E\setminus F$ and $i\in N_{e}(B)$\\
-    only if: for all $i$ and $e$: $p_{i}^{e} \leq \Delta_{i}^{e}(B)$
-      and $c_{e}(B) = \sum_{i\in N_{e}(B)}p_{i}^{e}$
-  \end{proof}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Existence of Pure Nash Equilibria}
-  \begin{theorem}
-    Every weighted matroid resource buying game with marginally non-increasing
-    cost functions possesses a pure Nash equilibria.
-  \end{theorem}
-  \begin{itemize}
-    \item socially optimal configuration profile: $B\in\mathcal{B}$ such that
-      $\sum_{e\in E}c_{e}(\ell_{e}(B))$ is minimal
-    \item for socially optimal configuration profile $B$ holds:
-      \begin{equation*}
-        c_{e}(B)\leq \sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B)
-        \text{ for all }e\in E\setminus F
-      \end{equation*}
-    \item $B$ is a pure Nash equilibrium
-    \item (but finding socially optimal configuration profiles is NP-hard)
-  \end{itemize}
-\end{frame}
-
-\section{Non-Matroid Strategy Spaces}
-\begin{frame}
-\frametitle{Consequences of using Non-Matroid Strategy Spaces}
-  \begin{lemma}
-    If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there
-    exist $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
-    set $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains
-    $b$ and $c$. (Especially, there is $S\in\mathcal{S}$ with
-    $S\subseteq X\cup Y$ and $a\in S$ but $b,c\notin S$.)
-  \end{lemma}
-  \begin{theorem}
-    For every non-matroid anti-chain $\mathcal{S}$ on a set of resource $E$,
-    there exists a weighted two-player resource buying game
-    $G = \tupel{\tilde{E}, \tupel{\mathcal{S}_{1} \times
-    \mathcal{S}_{2}}\times \mathcal{P}, \pi}$ having marginally non-increasing
-    cost functions, whose strategy spaces $\mathcal{S}_{1}$ and
-    $\mathcal{S}_{2}$ are both isomophic to $\mathcal{S}$, so that $G$ does not
-    possess a pure Nash equilibrium.
-  \end{theorem}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Construction of games without PNE}
-
-\end{frame}
-
-\section{Conclusion}
-\begin{frame}
-\end{frame}
-
 \end{document}

### 2017-02-28 paper.tex
proceeded on paper, added algorithm on separated pdf for transparency print

@@
 can be used to again obtain a spanning tree\footnote{see Figure
-\ref{fig:spanning} for an illustration}. Consider the algorithm of Prim
-which computes spanning trees by iteratively adding edges which do not close a
-cycle: every added edge works towards a basis in $\mathcal{S}$ and opens a
-dimensionality by connecting one of the graph nodes.
+\ref{fig:spanning} for an illustration}.
 \begin{figure}
@@
 introduce cuts and contractions and deletions}
+Consider the algorithm of Prim which computes spanning trees by iteratively
+adding edges which do not close a cycle: every added edge works towards a basis
+in $\mathcal{S}$ and opens a dimensionality by connecting one of the graph
+nodes. When an edge is added the result of the algorithm can only compute
+certain spanning trees, namely those which contain all edges added up to this
+point. Fixing certain elements in matroids and therefore restricting the set of
+\enquote{useable} bases is captured by the \emph{contraction} operation on
+matroids.
+\begin{defi}
+  For a matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$ and one $e\in E$ we call
+  the matroid $\tupel{E\setminus\set{e}, \set{B\subseteq
+  (E\setminus\set{e})\middle| B\cup\set{e}\in\mathcal{B}}}$ the
+  \emph{contraction} of $e$ in $\mathcal{M}$, denoted by $\mathcal{M}/e$.
+\end{defi}
+In a similar manner we introduce the \emph{deletion} operation on matroids to
+disregard all bases which use a certain element.
+\begin{defi}
+  For a matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$ and one $e\in E$ we call
+  the matroid $\tupel{E\setminus\set{e}, \set{C\subseteq
+  (E\setminus\set{e})\middle| B\in\mathcal{B}}}$ the \emph{deletion} of $e$ in
+  $\mathcal{M}$, denoted by $\mathcal{M}\setminus e$.
+\end{defi}
+Note that this deletion operation is not necessarily well defined for all
+elements of the ground-set, e.g. deletion of an edge in the spanning tree
+matroid which is a bridge yields an empty set of bases and thus no valid
+matroid.
 

### 2017-02-28 paper.tex
added cuts

--- 2017-02-21 paper.tex
@@
 \begin{document}
+\input{tikz/settings}
 \maketitle
+\section{Introduction}
 
-\begin{defi}[Marginally non-increasing]
-  Whoop
+\section{Matroids}
+In this section we present the combinatorial structure of Matroids.
+\todo{why matroids?}
+
+We use matroids as a generalisation of the concept of linear independence.
+Matroids can be defined as a ground-set and the family of linear
+independent sets of this ground-set. This family has to satisfy three
+properties, i.e.
+\begin{enumerate}
+  \item the empty set is linear independent,
+  \item all subset of a linear independent set are linear independent and
+  \item for two linear independent sets we can find an element of the larger
+    set that forms a linear independent set when added to the smaller set.
+\end{enumerate}
+We use an equivalent definition of matroids which in a way captures the idea of
+having a vector space by giving instead of linear independent sets the bases of
+the ground-set.
+\begin{defi}
+  The structure $\tupel{E, \mathcal{B}}$ with $\mathcal{B}\subseteq 2^{E}$ is
+  a matroid if
+  \begin{enumerate}
+    \item $\mathcal{B}\neq\emptyset$
+    \item let $B,B'\in\mathcal{B}$ and for every $x\in B$ there is $y\in B'$
+      s. t. $(B\setminus\set{x})\cup\set{y}\in\mathcal{B}$
+  \end{enumerate}
 \end{defi}
+In analogy to vector spaces we consider every element of a basis to open access
+to a dimension. We illustrate this concept with the following example: given an
+undirected connected graph $G = \tupel{V, E}$ we will argue that
+$\tupel{E, \mathcal{S}}$ with $\mathcal{S}$ as edge-sets of spanning trees
+in $G$ forms a matroid. In order to meet the requirement that $\mathcal{S}$
+must not be empty we restrict $G$ to those graphs with at least two distinct
+vertices. Furthermore, given two spanning trees $\tupel{V, S_{1}}$ and
+$\tupel{V, S_{2}}$ of $G$ then removing an edge from $S_{1}$ yields a subgraph
+of $G$ that is separated into two connected components. Since $S_{2}$ forms a
+spanning tree as well there must be an edge connecting these components which
+can be used to again obtain a spanning tree\footnote{see Figure
+\ref{fig:spanning} for an illustration}.
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (t) {\input{tikz/graphp1}};
+      \node[below left=of t] {\input{tikz/graphp1S1}};
+      \node[below =of t] {\input{tikz/graphp1S2}};
+      \node[below right=of t] {\input{tikz/graphp1S1}};
+    \end{tikzpicture}
+  \end{center}
+  \caption{Graph with its spanning trees.}
+  \label{fig:spanning}
+\end{figure}
+\todo[done]{working iteratively towards a basis by prim's algorithm as example
+to introduce cuts and contractions and deletions}
+Consider the algorithm of Prim which computes spanning trees by iteratively
+adding edges which do not close a cycle: every added edge works towards a basis
+in $\mathcal{S}$ and opens a dimensionality by connecting one of the graph
+nodes. When an edge is added the result of the algorithm can only compute
+certain spanning trees, namely those which contain all edges added up to this
+point. Fixing certain elements in matroids and therefore restricting the set of
+\enquote{useable} bases is captured by the \emph{contraction} operation on
+matroids.
+\begin{defi}
+  For a matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$ and one $e\in E$ we call
+  the matroid $\tupel{E\setminus\set{e}, \set{B\subseteq
+  (E\setminus\set{e})\middle| B\cup\set{e}\in\mathcal{B}}}$ the
+  \emph{contraction} of $e$ in $\mathcal{M}$, denoted by $\mathcal{M}/e$.
+\end{defi}
+In a similar manner we introduce the \emph{deletion} operation on matroids to
+disregard all bases which use a certain element.
+\begin{defi}
+  For a matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$ and one $e\in E$ we call
+  the matroid $\tupel{E\setminus\set{e}, \set{C\subseteq
+  (E\setminus\set{e})\middle| B\in\mathcal{B}}}$ the \emph{deletion} of $e$ in
+  $\mathcal{M}$, denoted by $\mathcal{M}\setminus e$.
+\end{defi}
+Note that this deletion operation is not necessarily well defined for all
+elements of the ground-set, e.g. deletion of an edge in the spanning tree
+matroid which is a bridge yields an empty set of bases and thus no valid
+matroid. Analogously, any set of edges that, when removed, disconnect the graph
+contains at least one element necessarily present in any basis. We call such
+sets cuts\footnote{see Figure \ref{fig:cuts} for an illustration} and define
+them as follows.
+\begin{defi}
+  Let $\mathcal{M} = \tupel{E, \mathcal{B}}$ be a matroid. A \emph{cut}
+  $C\subseteq E$ is an inclusion-wise minimal set s.t. $E\setminus C$ does not
+  contain any basis in $\mathcal{B}$.
+\end{defi}
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (1) {\input{tikz/graphp1Cut1}};
+      \node[right=of 1] (2) {\input{tikz/graphp1Cut2}};
+      \node[right=of 2] (3) {\input{tikz/graphp1Cut3}};
+      \node[below=of 1] (4) {\input{tikz/graphp1Cut4}};
+      \node[right=of 4] (5) {\input{tikz/graphp1Cut5}};
+    \end{tikzpicture}
+  \end{center}
+  \caption{Cuts of the spanning tree matroid from the graph presented in Figure
+    \ref{fig:spanning}.}
+  \label{fig:cuts}
+\end{figure}
+
+\todos
 

### 2017-03-01 paper.tex
introduced congestion model

@@
 \usepackage{todo}
+\usepackage{amsmath}
 \usepackage[framed]{ntheorem}
@@
 
+\section{Congestion Model}
+In this section we want to introduce a structure to model resources and demands
+of actors on resources. Therefore, we consider a set of players $N$ and a set
+of resources $E$. Every player has a personal aim which can be achieved by
+different resources. This is modelled for a player $i\in N$ as family
+$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
+want to account for different demands of players on resources by fixing a
+demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
+resource depends on the load the players put onto the resource modelled as
+individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
+resource $e\in E$. As an example consider different actors that build a shared
+network infrastructure. The connections in the network are resources, the
+actors are the players which have individual spots they want to connect.
+Different actors might need different bandwidth for connections, i.e. their
+demands, and the cost for using connections depends on the used bandwidth.
+Accordingly we obtain a congestion model
+\begin{equation*}
+  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
+  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
+\end{equation*}
+for which we introduce some additional definitions:
+\begin{itemize}
+  \item for a profile $S\in\mathcal{S}$ we define
+    the demand on resource $e$ for $S$ as
+    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
+  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
+    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
+\end{itemize}
+\todo{complete list of auxilary definitions}
+
 \section{Matroids}
@@
 We use an equivalent definition of matroids which in a way captures the idea of
-having a vector space by giving instead of linear independent sets the bases of
-the ground-set.
+bases of a vector space by giving the inclusion-wise maximal linear independent
+sets (in analogy also called bases).
 \begin{defi}
@@
 
+\section{Unweighted Matroid Games}
+
 \todos

### 2017-03-01 paper.tex
game def

@@
 \end{itemize}
-\todo{complete list of auxilary definitions}
 
+The cost that results from a profile $S\in\mathcal{S}$ is covered by all
+players. To model this we consider the game 
+\begin{equation*}
+  G = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
+\end{equation*}
+where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
+$\mathcal{P}_{i} = |\mathbb{R}_{+}^{|E|}|$ to model how much every player
+contributes in paying for the cost of every resource. We denote the element
+from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
+under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
+$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
+every player for a strategy profile $\tupel{S, p}$ by
+\begin{equation*}
+  \pi_{i}(S, p) = \begin{cases}
+    \sum_{e\in E}p_{i}^{e} &\text{ if $S_{i}$ is bought under
+    $\tupel{S, p}$ (i.e. all $e\in S_{i}$ are bought)}\\
+    \infty &\text{ otherwise}
+  \end{cases}
+\end{equation*}
+Thus, every player tries to minimise her personal contribution to the costs
+but ensures that her demand is satisfied.
 \section{Matroids}

### 2017-03-02 paper.tex
unweighted game

@@
 resource depends on the load the players put onto the resource modelled as
-individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
-resource $e\in E$. As an example consider different actors that build a shared
-network infrastructure. The connections in the network are resources, the
-actors are the players which have individual spots they want to connect.
+individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{R}_{+}$ for
+every resource $e\in E$. As an example consider different actors that build a
+shared network infrastructure. The connections in the network are resources,
+the actors are the players which have individual spots they want to connect.
 Different actors might need different bandwidth for connections, i.e. their
@@
     $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
+  \item we call $c_{e}$ \emph{marginally non-increasing} if
+    $c_{e}(y + \delta) - c_{e}(y) \leq c_{e}(x + \delta) - c_{e}(x)$ holds
+    for all $x,y,\delta\in N$ with $x\leq y$
+  \item analogously $c_{e}$ is \emph{marginally non-decreasing} if
+    $c_{e}(y + \delta) - c_{e}(y) \geq c_{e}(x + \delta) - c_{e}(x)$ holds
+    for all $x,y,\delta\in N$ with $x\leq y$
 \end{itemize}
+Note that linear and constant cost functions are marginally non-increasing.
 
 The cost that results from a profile $S\in\mathcal{S}$ is covered by all
-players. To model this we consider the game 
+players. To model this we consider the resource buying game 
 \begin{equation*}
@@
 
-\section{Unweighted Matroid Games}
+\section{Unweighted Matroid Games with marginally non-increasing cost
+functions}
+We present an algorithm which computes pure Nash equilibria in unweighted
+matroid games with marginally non-increasing cost functions. Firstly, an
+unweighted matroid game builds upon a congestion model of the form
+$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
+(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
+(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
+$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
+given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
+functions $c_{e}$ are marginally non-increasing. The algorithm
+we present in the following chooses a basis for every player by iteratively
+adding one element from a cut and contracting the matroid to the added element
+while deleting all other elements from the cut. Since cuts are inclusion-wise
+minimal deleting all but one element from one cut leaves at least one possible
+basis for the player available.
 

### 2017-03-02 paper.tex
started alg

@@
 minimal deleting all but one element from one cut leaves at least one possible
-basis for the player available.
+basis for the player available. For every player we maintain the elements which
+are chosen for her up to the current state (\emph{working basis}) and which
+elements are still available to build her basis (\emph{ground-set}) and which
+bases she can still use. Initially the working basis is empty and the
+ground-set and available bases are taken from the matroid of the player. For
+every resource we maintain the cost the next added load causes and how much
+load already is placed upon the resource(\emph{current load}). Initially for
+every resource $e$ the current load is zero and the next load causes $c_{e}(1)$
+cost.
 

### 2017-03-02 slides.tex
a few small corrections
started work on paper
last slide polish

@@
 \author[C. Welzel]{Christoph Welzel}
+\date{March 3, 2017}
 
@@
       \item<3-> Payoff for a player depends on what she payed to meet her demands
-        of resources
     \end{itemize}
@@
 \begin{frame}
-  \frametitle{Definition: congestion model}
+  \frametitle{Definition: Congestion Model}
   \begin{equation*}
@@
       \end{itemize}
-    \item<5-> $c_{e}:\mathbb{N}\rightarrow\mathbb{N}$ with
+    \item<5-> $c_{e}:\mathbb{N}\rightarrow\mathbb{R}_{+}$ with
       $c_{e}(S) = c_{e}(\ell_{e}(S))$: cost for the resource $e$ under the load
@@
 \begin{frame}
-  \frametitle{Definition: weighted resource buying game}
+  \frametitle{Definition: Weighted Resource Buying Game}
   \begin{equation*}
@@
       $P_{i} = \mathbb{R}^{|E|}_{+}$: payment of player $i$
-    \item<3-> $e\in E$ is bought under $S\in \mathcal{S}$ if
+    \item<3-> $e\in E$ \emph{is bought under $S\in \mathcal{S}$} if
       $\sum_{i\in N}p_{i}^{e} \geq c_{e}(S)$
@@
 \begin{frame}
-  \frametitle{A few simplifications}
+  \frametitle{Restricted Setup}
   \begin{itemize}
@@
 \begin{frame}
-  \frametitle{Operations on Matroids $\mathcal{M} = \tupel{E, \mathcal{B}}$}
+  \frametitle{Operations on Matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$}
   \begin{columns}
@@
         \item<5-> assume there is a beneficial alternative basis
-          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
+          $\hat{B} = (B_{i}\setminus\set{g})\cup{\set{f}}$
           \begin{itemize}
@@
           \set{f\in E\setminus\set{e}\middle|
-          (B_{i}\setminus{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
+          (B_{i}\setminus\set{e})\cup\set{f}\in\mathcal{B}_{i}}$: set of resources
           that can replace $e$ for player $i$

### 2017-03-31 paper.tex
added alg

@@
 \end{figure}
-\todo[done]{working iteratively towards a basis by prim's algorithm as example
-to introduce cuts and contractions and deletions}
-Consider the algorithm of Prim which computes spanning trees by iteratively
+\todo[done]{working iteratively towards a basis by kruskal's algorithm as
+example to introduce cuts and contractions and deletions}
+Consider the algorithm of Kruskal which computes spanning trees by iteratively
 adding edges which do not close a cycle: every added edge works towards a basis
-in $\mathcal{S}$ and opens a dimensionality by connecting one of the graph
-nodes. When an edge is added the result of the algorithm can only compute
+in $\mathcal{S}$ and opens a dimensionality by connecting already computed
+components.  When an edge is added the result of the algorithm can only compute
 certain spanning trees, namely those which contain all edges added up to this
@@
 given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
-functions $c_{e}$ are marginally non-increasing. The algorithm
-we present in the following chooses a basis for every player by iteratively
-adding one element from a cut and contracting the matroid to the added element
-while deleting all other elements from the cut. Since cuts are inclusion-wise
-minimal deleting all but one element from one cut leaves at least one possible
-basis for the player available. For every player we maintain the elements which
-are chosen for her up to the current state (\emph{working basis}) and which
-elements are still available to build her basis (\emph{ground-set}) and which
-bases she can still use. Initially the working basis is empty and the
-ground-set and available bases are taken from the matroid of the player. For
-every resource we maintain the cost the next added load causes and how much
-load already is placed upon the resource(\emph{current load}). Initially for
-every resource $e$ the current load is zero and the next load causes $c_{e}(1)$
-cost.
+functions $c_{e}$ are marginally non-increasing.
+
+The algorithm we present in the following chooses a basis for every player by
+iteratively adding one element from a cut and contracting the matroid to the
+added element while deleting all other elements from the cut. Since cuts are
+inclusion-wise minimal deleting all but one element from one cut leaves at
+least one possible basis for the player available. For every player we maintain
+the elements which are chosen for her up to the current state
+(\emph{working basis}) and which elements are still available to build her
+basis (\emph{ground-set}) and which bases she can still use. Initially the
+working basis is empty and the ground-set and available bases are taken from
+the matroid of the player. For every resource we maintain the cost the next
+added load causes and how much load already is placed upon the
+resource(\emph{current load}). Initially for every resource $e$ the current
+load is zero and the next load causes $c_{e}(1)$ cost. We can devide the
+algorithm into four steps as presented in Figure \ref{alg:main}.
+\begin{figure}
+  \begin{tabular}{|lll|}
+    \hline
+    (i) & Init: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item \parbox{0.7\textwidth}{every player: empty working basis,
+            complete ground-set, complete set of valid result bases}
+          \item every resource: cost for next load, current load
+        \end{itemize}
+      }\\\hline
+    (ii) & Find: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item inclusion-min (necessary cost)-max cut $C$
+          \item minimal cost resource $e$ in $C$
+          \item owner $i$ of $C$
+        \end{itemize}
+      }\\\hline
+    (iii) & Pick: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item $i$: add $e$ to working basis, contract matroid to $e$
+          \item $e$: update marginal cost and increase load
+          \item all player: delete elements $C\setminus\set{e}$ from matroid
+        \end{itemize}
+      }\\\hline
+    (iv) & Break: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
+        \begin{itemize}
+          \item exists player with incomplete basis: goto (ii)
+          \item otherwise: return chosen bases and payments
+        \end{itemize}
+      }\\\hline
+  \end{tabular}
+  \caption{Algorithm to compute a PNE for unweighted matroid games with
+    marginally non-increasing cost functions. Note that in step (ii) only
+    inclusion-wise minimal cuts are considered (specifically the one for which
+    minimal cost of all elements in the cut is maximal over all considered cuts
+    is chosen). Restricting the selection to inclusion-wise minimal cuts
+    ensures that removing all other elements preserves possible bases for
+    \emph{all} players}
+  \label{alg:main}
+\end{figure}
+By induction on the iterations one can prove that the cost of the chosen
+element in step (ii) always decreases. This is a key lemma to prove the
+correctness of the algorithm. Because, if we assume to have a beneficial
+alternative to the computed basis for one player there is an element with
+less cost. This alternative element is not part of the selected cut since
+it would be removed for all players and thus keep its marginal cost although
+only elements with higher costs are removed (by choice of the element in the
+cut). Furthermore, the alternative element cannot be available to the player
+for which the cut is selected since both elements open the
+\enquote{same dimensionality} in contradiction to choosing a cut. Thus, the
+alternative element has been removed before which implies less cost in a
+previous step to the iteration where the original element was chosen. This
+contradicts the monotonicity of costs of considered elements through the
+iterations. Thus
+\begin{theo}
+  The presented algorithm computes a PNE.
+\end{theo}
+
+\section{Weighted Matroid Games}
 

### 2017-04-02 paper.tex
weighted games

@@
 \section{Weighted Matroid Games}
+Starting from a congestion model where every player aims to buy a basis from
+a certain matroid and every player puts an individual demand upon the resources
+she/he uses we derive a complete characterisation of PNEs as well as show that
+every socially optimal solution actually induces a PNE. Firstly, we give some
+auxiliary definitions (with a profile $B\in\mathcal{B}$, a resource $e\in E$):
+\begin{itemize}
+  \item $N_{e}(B) = \set{i\in N\middle| e\in B_{i}}$ is the set of players
+    which use resource $e$ in the profile $B$
+  \item $\ex_{i}(e) = \set{f\in E\setminus\set{e}\middle|
+    (B_{i}\setminus\set{e})\cup\set{f}\in\mathcal{B}_{i}}$ is the set of
+    resources player $i\in N_{e}(B)$ could exchange $e$ with
+  \item $F$ is the set of resources that is obligatory for any player, i.e.
+    every element of $F$ is present in \emph{all} bases of one (or more) player
+  \item $\Delta_{i}\tupel{B;e\rightarrow f}$ is the marginal cost player $i$
+    has to pay for resource $f$ if he intends to use $f$ instead of $e$
+    (we define the minimum over all resources $e$ can be exchanged with as
+    $\Delta_{i}^{e}(B) = \min_{f\in\ex_{i}(e)}\Delta_{i}(B;e\rightarrow f)$)
+\end{itemize}
+With these definitions we can formulate the following characterisation of
+PNEs which holds for all non-negative and non-decreasing cost functions.
+\begin{theo}
+  For a weighted matroid resource buying game $\tupel{N, E, \mathcal{B}, d, c}$
+  there is a payment vector $p$ s.t. $\tupel{B\in\mathcal{B}, p}$ is a PNE
+  if and only if
+  \begin{equation*}
+    c_{e}(B)\leq\sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B) \text{ for all } e\in
+    E\setminus F
+  \end{equation*}
+\end{theo}
+The \enquote{only if} direction is easily given by the fact that the cost
+of a resource is the sum of the contributions of every player for this resource
+and no player has an incentive to uniliterally change to another basis of
+her/his matroid. While, for the \enquote{if} direction, we let for elements in
+$F$ one player for whom this resource is obligatory pay for this resource
+(since she/he needs this resource to be available she/he can not choose to
+uniliterally change her/his payment). For all other elements we can define the
+payments as follows:
+\begin{equation*}
+  p_{i}^{e} = \begin{cases}
+    0 &\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) = 0\\
+    \underbrace{
+      \frac{c_{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}
+    }_{\leq 1}\cdot\Delta_{i}^{e}(B) &\text{ otherwise}
+  \end{cases}
+\end{equation*}
+which yields $p_{i}^{e}\leq \Delta_{i}^{e}$ for all $e\in E\setminus F$
+implying a PNE.
+
+Using this one can derive a series of inequalities to show that every socially
+optimal solution satisfies the given characterisation and hence
+\begin{theo}
+  Every weighted matroid resource buying game with marginally non-increasing
+  cost functions posses a PNE.
+\end{theo}
+For completeness we present - without going into details - an analogous result
+for non-decreasing cost functions. Again starting from a socially optimal
+configuration one can derive a pricing vector (called marginal cost pricing)
+which forms with the given configuration a PNE. Especially this result is
+also viable for non-matroid strategy spaces, yielding:
+\begin{theo}
+  Let $G$ be a weighted resource buying game with non-decreasing marginal costs
+  and let $S^{\ast}$ be a socially optimal solution. Then, marginal cost
+  pricing induces a PNE.
+\end{theo}
 

### 2017-04-02 paper.tex
started on non-matroid strategy spaces

@@
 
+\section{Non-Matroid Strategy Spaces}
+Finally, we consider in this section non-matroid strategy spaces. Specifically,
+we present a construction which illustrates how to obtain a weighted two player
+resource buying game with marginally non-increasing cost functions which does
+not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
+matroids are exactly the structures to consider using marginally non-increasing
+cost functions since other structures cannot guarantee the existence of PNEs.
+
 \todos

### 2017-04-02 paper.tex
theorem non-matroid strategy space

@@
 cost functions since other structures cannot guarantee the existence of PNEs.
+Thus, we prove the following theorem:
+\begin{theo}
+  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
+  there exists a weighted two-player resource buying game
+  $G = \tupel{\tilde{E},
+    (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
+  having marginally non-increasing cost functions, whose strategy spaces
+  $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ are both isomorphic to $\mathcal{S}$,
+  so that $G$ does not posses a PNE.
+\end{theo}
 

### 2017-04-02 paper.tex
first 'feature complete' text

--- 2017-04-02 paper.tex
@@
 \newframedtheorem{theo}{Theorem}
+\newframedtheorem{lemma}{Lemma}
 
@@
 
+\section{Non-Matroid Strategy Spaces}
+Finally, we consider in this section non-matroid strategy spaces. Specifically,
+we present a construction which illustrates how to obtain a weighted two player
+resource buying game with marginally non-increasing cost functions which does
+not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
+matroids are exactly the structures to consider using marginally non-increasing
+cost functions since other structures cannot guarantee the existence of PNEs.
+Thus, we prove the following theorem:
+\begin{theo}
+  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
+  there exists a weighted two-player resource buying game
+  $G = \tupel{\tilde{E},
+    (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
+  having marginally non-increasing cost functions, whose strategy spaces
+  $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ are both isomorphic to $\mathcal{S}$,
+  so that $G$ does not posses a PNE.
+\end{theo}
+As said before we start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which
+specifically does \emph{not} satisfy the matroid properties. Hence
+$\mathcal{S}$ contains two sets $X, Y$ s.t. there is one element in $X$ for
+which we cannot find a single element in $Y$ to obtain an element from
+$\mathcal{S}$ again. Intuitively, the dimension of one element in $X$ needs
+two elements from $Y$ to be become available. This can be formally described
+by the following lemma:
+\begin{lemma}
+  If $\mathcal{S}\subseteq 2^{E}$ is a non-matroid anti-chain, then there exist
+  $X,Y\in\mathcal{S}$ and $\set{a,b,c}\subseteq X\cup Y$ such that each
+  $Z\in\mathcal{S}$ with $Z\subseteq(X\cup Y)\setminus\set{a}$ contains both,
+  $b$ and $c$.
+\end{lemma}
+Especially we can guarantee that there are two elements in $\mathcal{S}$ s.t.
+one contains $a$ (but not $b$ and $c$) and the other $b$ and $c$ (but not $a$).
+In the following we construct a game which does not possess a PNE. The
+constructed game is illustrated in Figure \ref{fig:game} for better
+understanding.
+\begin{figure}
+  \input{tikz/gamediagram}
+  \caption{Illustration of constructed game which does not possess a PNE.}
+  \label{fig:game}
+\end{figure}
+We consider two isomorphic copies of $\mathcal{S}$:
+$\mathcal{S}_{1},\mathcal{S}_{2}$ and by previous lemma there are
+$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We interleaf
+the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by precisely three
+elements $x,y,z$ which we identify in both copies differently. Namely, we set
+$x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and $z = c_{1} = c_{2}$. The set of
+resources for $G$ is now the union of both ground-sets w.r.t. the intersection
+which is $\set{x,y,z}$. Furthermore we fix the cost functions of all elements
+in $\tilde{E}\setminus{X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2}}$ to a high constant
+$M$ which ensures that both players only play within $X_{i}, Y_{i}$ (for
+$i = 1,2$ respectively). In this \enquote{sub-arena} we set the cost functions
+of all elements other than $\set{x,y,z}$ to $0$ regardless of the demand. And
+concludingly we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$, and
+$c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and
+$d_{2} = 4$. Thus, each player either contributes to pay for her/his $a$ or
+to $b$ and $c$. Assuming there is a PNE
+$\tupel{Z^{\ast} = \tupel{Z_{1}^{\ast}, Z_{2}^{\ast}},
+p^{\ast} = \tupel{p_{1}^{\ast}, p_{2}^{\ast}}}$ we can conclude by the choice
+of $\set{x,y,z}$ that
+\begin{equation*}
+  x\notin Z_{1}^{\ast}\Rightarrow \set{y,z}\subseteq Z_{1}^{\ast} \text{ and }
+  y\notin Z_{2}^{\ast}\Rightarrow \set{x,z}\subseteq Z_{2}^{\ast}
+\end{equation*}
+By examining the restricted environment of the cost inducing elements ($x,y,z$)
+and the conclusion that one player either only contributes to $x$ or $y$ and
+$z$ and the other only to $y$ or $x$ and $z$ one can conclude that neither
+$x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a contradiction to
+the existence of a PNE and thus concludes the argument on the section-leading
+theorem.
+
 \todos

### 2017-04-03 paper.tex
added introduction and conclusion

@@
 \usepackage[framed]{ntheorem}
+\usepackage[style=numeric]{biblatex}
 
@@
 \newframedtheorem{lemma}{Lemma}
+
+\addbibresource{bibliography.bib}
 
@@
 \begin{document}
+
 \input{tikz/settings}
@@
 \section{Introduction}
+In this paper we examine a certain class of games based on congestion models.
+Intuitively speaking we consider a set of resources and actors with individual
+demands on this set of resources. We model this competing behaviour of actors
+in terms of strategic games which are applicable for analysis in regards of
+Nash equilibria. Mainly, we are interested in the existence and computability
+of pure Nash equilibria (PNE), i.e. a state where each actor has no interest
+to uniliterally change her/his behaviour if all other players stick to their
+strategy. We examine congestion models with different cost functions of
+resource, different structures of resources each player wants to be available
+and different demand of players on her/his resources. As main results we prove
+the existence of PNE for
+\begin{itemize}
+  \item matroid games with marginally non-increasing cost functions
+  \item congestion games with marginally non-decreasing cost functions
+\end{itemize}
+In terms of complexity we present an algorithm to compute a PNE for unweighted
+(i.e. uniform demands for all players) matroid games with marginally
+non-increasing cost functions. Additionally, we construct for non-matroid
+structures congestion games with marginally non-increasing cost functions which
+specifically do not allow for PNEs. This paper only presents results and
+arguments from \cite{main}. Specifically we focus on intuitions and thus
+present proofs not in exhaustive detail but try to conway the central ideas.
+
+We start with defining an appropiate congestion model and an associated
+strategic game as well as introducing matroids as combinatorial structure
+to model desired configurations of resources for players. Following an
+algorithm to compute PNEs in unweighted matroid games with marginally
+non-increasing cost functions as well as its correctness proof is presented.
+Afterwards weighted matroid games with different cost functions are examined
+and concludingly, we study non-matroid configuration spaces.
 
@@
 where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
-$\mathcal{P}_{i} = |\mathbb{R}_{+}^{|E|}|$ to model how much every player
+$\mathcal{P}_{i} = \mathbb{R}_{+}^{|E|}$ to model how much every player
 contributes in paying for the cost of every resource. We denote the element
@@
 Thus, every player tries to minimise her personal contribution to the costs
-but ensures that her demand is satisfied.
+but ensures that her/his demand is satisfied.
 \section{Matroids}
-In this section we present the combinatorial structure of Matroids.
+In this section we present the combinatorial structure of matroids
 \todo{why matroids?}
-
-We use matroids as a generalisation of the concept of linear independence.
+which we use as a generalisation of the concept of linear independence.
 Matroids can be defined as a ground-set and the family of linear
@@
 example to introduce cuts and contractions and deletions}
-Consider the algorithm of Kruskal which computes spanning trees by iteratively
-adding edges which do not close a cycle: every added edge works towards a basis
-in $\mathcal{S}$ and opens a dimensionality by connecting already computed
-components.  When an edge is added the result of the algorithm can only compute
-certain spanning trees, namely those which contain all edges added up to this
-point. Fixing certain elements in matroids and therefore restricting the set of
-\enquote{useable} bases is captured by the \emph{contraction} operation on
-matroids.
+Consider the algorithm of Kruskal \cite{kruskal} which computes spanning trees
+by iteratively adding edges which do not close a cycle: every added edge works
+towards a basis in $\mathcal{S}$ and opens a dimensionality by connecting
+already computed components. When an edge is added the result of the algorithm
+can only compute certain spanning trees, namely those which contain all edges
+added up to this point. Fixing certain elements in matroids and therefore
+restricting the set of \enquote{useable} bases is captured by the
+\emph{contraction} operation on matroids.
 \begin{defi}
@@
 In a similar manner we introduce the \emph{deletion} operation on matroids to
-disregard all bases which use a certain element.
+disregard all bases which use a certain element (in Kruskal's algorithm upon
+adding an edge we can remove all other edges connecting the same components).
 \begin{defi}
@@
 \end{defi}
-Note that this deletion operation is not necessarily well defined for all
-elements of the ground-set, e.g. deletion of an edge in the spanning tree
-matroid which is a bridge yields an empty set of bases and thus no valid
-matroid. Analogously, any set of edges that, when removed, disconnect the graph
-contains at least one element necessarily present in any basis. We call such
-sets cuts\footnote{see Figure \ref{fig:cuts} for an illustration} and define
-them as follows.
+In the context of graphs and the spanning tree matroids the contraction and
+deletion operation corresponds to the contraction of two nodes connected by
+an edge and the deletion of an edge respectively. Note that a deletion
+operation is not necessarily well defined for all elements of the ground-set,
+e.g. deletion of an edge in the spanning tree matroid which is a bridge yields
+an empty set of bases and thus no valid matroid. Analogously, any set of edges
+that, when removed, disconnect the graph contains at least one element
+necessarily present in any basis. We call such sets cuts\footnote{see Figure
+\ref{fig:cuts} for an illustration} and define them as follows.
 \begin{defi}
@@
     ensures that removing all other elements preserves possible bases for
-    \emph{all} players}
+    \emph{all} players. Also the algorithm terminates in at most $|N|\cdot|E|$
+    iterations (each iteration disgards at least one element for one player).
+    For a more detailed pseudo-code representation and an description of how to
+    compute the minimal cut and the minimal cost element within we refer to
+    \cite[Algorithm 1 and 3.3 A Subroutine to Detect $C^{\ast}, e^{\ast}$ and
+    $i^{\ast}$]{main}.}
   \label{alg:main}
@@
 \end{theo}
-For completeness we present - without going into details - an analogous result
+For completeness we state - without going into details - an analogous result
 for non-decreasing cost functions. Again starting from a socially optimal
@@
 $\mathcal{S}$ again. Intuitively, the dimension of one element in $X$ needs
-two elements from $Y$ to be become available. This can be formally described
+two elements from $Y$ to become available. This can be formally described
 by the following lemma:
@@
 which is $\set{x,y,z}$. Furthermore we fix the cost functions of all elements
-in $\tilde{E}\setminus{X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2}}$ to a high constant
+in $\tilde{E}\setminus(X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2})$ to a high constant
 $M$ which ensures that both players only play within $X_{i}, Y_{i}$ (for
@@
 
+\section{Conclusion}
+Among other restrictions we studied unweighted congestion games with marginally
+non-increasing cost functions. For these games matroids are precisely the
+configuration spaces to guarantee PNEs as well as allow for efficient
+computation of one PNE. For weighted matroid games with marginally
+non-increasing cost functions the existence of PNEs can be assured. Also for
+weighted congestion games with marginally non-decreasing cost functions PNEs
+are given. Hereby the structure of strategy spaces is unrestricted.
+Concludingly, marginally non-increasing cost functions demand matroid strategy
+spaces as combinatorial structure which capture e.g. spanning trees, linear
+independence, \dots. On the other hand marginally non-decreasing cost functions
+might induce a certain stability in a market by ensuring the existence of PNEs.
+
+\printbibliography
+
 \todos

### 2017-04-07 paper.tex
removed todos
polished

@@
 \usepackage{framed}
-\usepackage{todo}
+\usepackage[hide]{todo}
 \usepackage{amsmath}
@@
 In this paper we examine a certain class of games based on congestion models.
-Intuitively speaking we consider a set of resources and actors with individual
+Intuitively speaking, we consider a set of resources and actors with individual
 demands on this set of resources. We model this competing behaviour of actors
-in terms of strategic games which are applicable for analysis in regards of
+in terms of strategic games which are applicable for analysis regarding
 Nash equilibria. Mainly, we are interested in the existence and computability
 of pure Nash equilibria (PNE), i.e. a state where each actor has no interest
-to uniliterally change her/his behaviour if all other players stick to their
-strategy. We examine congestion models with different cost functions of
-resource, different structures of resources each player wants to be available
+to unilaterally change her/his behaviour if all other players stick to their
+strategy. We examine congestion models with different cost functions for
+resources, different structures of resources each player wants to be available
 and different demand of players on her/his resources. As main results we prove
@@
 (i.e. uniform demands for all players) matroid games with marginally
-non-increasing cost functions. Additionally, we construct for non-matroid
-structures congestion games with marginally non-increasing cost functions which
+non-increasing cost functions. Additionally, we construct congestion games for
+non-matroid structures with marginally non-increasing cost functions which
 specifically do not allow for PNEs. This paper only presents results and
-arguments from \cite{main}. Specifically we focus on intuitions and thus
-present proofs not in exhaustive detail but try to conway the central ideas.
+arguments from \cite{main}. Specifically, we focus on intuitions and thus
+present proofs not in exhaustive detail but try to convey the central ideas.
 
-We start with defining an appropiate congestion model and an associated
-strategic game as well as introducing matroids as combinatorial structure
-to model desired configurations of resources for players. Following an
-algorithm to compute PNEs in unweighted matroid games with marginally
-non-increasing cost functions as well as its correctness proof is presented.
-Afterwards weighted matroid games with different cost functions are examined
+We start by defining an appropiate congestion model and an associated
+strategic game as well as by introducing matroids as combinatorial structures
+to model desired configurations of resources for players. Following we present
+an algorithm to compute PNEs in unweighted matroid games with marginally
+non-increasing cost functions and its correctness proof.
+Afterwards, we examine weighted matroid games with different cost functions
 and concludingly, we study non-matroid configuration spaces.
@@
 \section{Congestion Model}
-In this section we want to introduce a structure to model resources and demands
+In this section, we introduce a structure to model resources and demands
 of actors on resources. Therefore, we consider a set of players $N$ and a set
 of resources $E$. Every player has a personal aim which can be achieved by
-different resources. This is modelled for a player $i\in N$ as family
+different resources. This is modelled for a player $i\in N$ as a family
 $\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
@@
 individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{R}_{+}$ for
-every resource $e\in E$. As an example consider different actors that build a
+every resource $e\in E$. As an example, consider different actors that build a
 shared network infrastructure. The connections in the network are resources,
-the actors are the players which have individual spots they want to connect.
+the actors are the players which have individual nodes they want to connect.
 Different actors might need different bandwidth for connections, i.e. their
 demands, and the cost for using connections depends on the used bandwidth.
-Accordingly we obtain a congestion model
+Accordingly, we obtain a congestion model
 \begin{equation*}
@@
     the demand on resource $e$ for $S$ as
-    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
+    $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
   \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
@@
 The cost that results from a profile $S\in\mathcal{S}$ is covered by all
-players. To model this we consider the resource buying game 
+players. This leads to a definition of resource buying game:
+\begin{defi}
+  For a congestion model $\mathcal{M} = \tupel{N, E, \mathcal{S},
+  \tupel{d_{i}}_{i\in N}, \tupel{c_{e}}_{e\in E}}$ we define a
+  \emph{resource buying game}
   \begin{equation*}
@@
   \end{equation*}
-where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
-$\mathcal{P}_{i} = \mathbb{R}_{+}^{|E|}$ to model how much every player
-contributes in paying for the cost of every resource. We denote the element
-from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
-under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
-$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
-every player for a strategy profile $\tupel{S, p}$ by
+  with $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
+  $\mathcal{P}_{i} = \mathbb{R}_{+}^{|E|}$ (which is the contribution of each
+  player to buy the demanded strategy profile).
+  We denote the element from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$
+  and call $e\in E$ \emph{bought} under $\tupel{S, p}\in
+  \mathcal{S}\times\mathcal{P}$ if $c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The
+  function $\pi$ defines the payoff for every player for a strategy profile
+  $\tupel{S, p}$ by
   \begin{equation*}
@@
   \end{equation*}
-Thus, every player tries to minimise her personal contribution to the costs
+\end{defi}
+Thus, every player tries to minimise her/his personal contribution to the costs
 but ensures that her/his demand is satisfied.
@@
 which we use as a generalisation of the concept of linear independence.
-Matroids can be defined as a ground-set and the family of linear
+Matroids can be defined as a ground-set and the family of linearly
 independent sets of this ground-set. This family has to satisfy three
@@
 \begin{enumerate}
-  \item the empty set is linear independent,
-  \item all subset of a linear independent set are linear independent and
-  \item for two linear independent sets we can find an element of the larger
-    set that forms a linear independent set when added to the smaller set.
+  \item the empty set is linearly independent,
+  \item all subsets of a linearly independent set are linearly independent and
+  \item for two linearly independent sets we can find an element of the larger
+    set that forms a linearly independent set when added to the smaller set.
 \end{enumerate}
-We use an equivalent definition of matroids which in a way captures the idea of
+We use an equivalent definition of matroids which captures the idea of
 bases of a vector space by giving the inclusion-wise maximal linear independent
@@
 Consider the algorithm of Kruskal \cite{kruskal} which computes spanning trees
-by iteratively adding edges which do not close a cycle: every added edge works
-towards a basis in $\mathcal{S}$ and opens a dimensionality by connecting
+by iteratively adding edges to a result which do not close a cycle in the
+subgraph induced by the edges in the result: every added
+edge works towards a basis in $\mathcal{S}$ and opens a dimension by connecting
 already computed components. When an edge is added the result of the algorithm
@@
   For a matroid $\mathcal{M} = \tupel{E, \mathcal{B}}$ and one $e\in E$ we call
-  the matroid $\tupel{E\setminus\set{e}, \set{C\subseteq
+  the matroid $\tupel{E\setminus\set{e}, \set{B\subseteq
   (E\setminus\set{e})\middle| B\in\mathcal{B}}}$ the \emph{deletion} of $e$ in
@@
 operation is not necessarily well defined for all elements of the ground-set,
-e.g. deletion of an edge in the spanning tree matroid which is a bridge yields
-an empty set of bases and thus no valid matroid. Analogously, any set of edges
-that, when removed, disconnect the graph contains at least one element
-necessarily present in any basis. We call such sets cuts\footnote{see Figure
-\ref{fig:cuts} for an illustration} and define them as follows.
-\begin{defi}
+e.g. deletion of an edge in the graph which is a bridge yields
+an empty set of bases in the spanning tree matroid and thus no valid matroid.
+Analogously, any set of edges that, when removed, disconnects the graph
+contains at least one element necessarily present in any basis. We call such
+sets cuts\footnote{see Figure \ref{fig:cuts} for an illustration} and define
+them as follows.  \begin{defi}
   Let $\mathcal{M} = \tupel{E, \mathcal{B}}$ be a matroid. A \emph{cut}
@@
 matroid games with marginally non-increasing cost functions. Firstly, an
-unweighted matroid game builds upon a congestion model of the form
+unweighted matroid game is based on a congestion model of the form
 $\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
@@
 least one possible basis for the player available. For every player we maintain
-the elements which are chosen for her up to the current state
+the elements which are chosen for her/him up to the current state
 (\emph{working basis}) and which elements are still available to build her
@@
 the matroid of the player. For every resource we maintain the cost the next
-added load causes and how much load already is placed upon the
-resource(\emph{current load}). Initially for every resource $e$ the current
-load is zero and the next load causes $c_{e}(1)$ cost. We can devide the
+added load causes and how much load already is placed on the resource
+(\emph{current load}). Initially, for every resource $e$ the current
+load is zero and the next load causes $c_{e}(1)$ cost. We can divide the
 algorithm into four steps as presented in Figure \ref{alg:main}.
 \begin{figure}
+  \begin{center}
     \begin{tabular}{|lll|}
@@
             \item $e$: update marginal cost and increase load
-          \item all player: delete elements $C\setminus\set{e}$ from matroid
+            \item all players: delete elements $C\setminus\set{e}$ from matroid
           \end{itemize}
@@
           \begin{itemize}
-          \item exists player with incomplete basis: goto (ii)
+            \item if exists player with incomplete basis: goto (ii)
             \item otherwise: return chosen bases and payments
@@
     \end{tabular}
+  \end{center}
   \caption{Algorithm to compute a PNE for unweighted matroid games with
@@
     iterations (each iteration disgards at least one element for one player).
-    For a more detailed pseudo-code representation and an description of how to
-    compute the minimal cut and the minimal cost element within we refer to
-    \cite[Algorithm 1 and 3.3 A Subroutine to Detect $C^{\ast}, e^{\ast}$ and
-    $i^{\ast}$]{main}.}
+    For a more detailed pseudo-code representation and a description of how to
+    compute the minimal cut and the minimal cost element in this cut we refer
+    to \cite[Algorithm 1 and 3.3 A Subroutine to Detect $C^{\ast}, e^{\ast}$
+    and $i^{\ast}$]{main}.}
   \label{alg:main}
 \end{figure}
-By induction on the iterations one can prove that the cost of the chosen
-element in step (ii) always decreases. This is a key lemma to prove the
-correctness of the algorithm. Because, if we assume to have a beneficial
-alternative to the computed basis for one player there is an element with
-less cost. This alternative element is not part of the selected cut since
-it would be removed for all players and thus keep its marginal cost although
-only elements with higher costs are removed (by choice of the element in the
-cut). Furthermore, the alternative element cannot be available to the player
-for which the cut is selected since both elements open the
-\enquote{same dimensionality} in contradiction to choosing a cut. Thus, the
-alternative element has been removed before which implies less cost in a
-previous step to the iteration where the original element was chosen. This
-contradicts the monotonicity of costs of considered elements through the
-iterations. Thus
+By induction on the number of iterations we can prove that the cost of the
+chosen element in step (ii) always decreases. This is a key insight to prove
+the correctness of the algorithm. Because, if we assume to have a beneficial
+alternative to the computed basis for one player there must exist an element
+with less cost. This alternative element cannot be part of the selected cut
+since it would be removed for all players and thus keep its marginal cost
+although only elements with higher costs are removed (by choice of the element
+in the cut). Furthermore, the alternative element cannot be available to the
+player for which the cut is selected since both elements open the
+\enquote{same dimension} in contradiction to the choice of a cut. Thus, the
+alternative element must already have been removed which implies less
+cost in a previous step to the iteration where the original element was chosen.
+This contradicts the monotonicity of costs of considered elements through the
+iterations. {Thus, we get the following theorem:
 \begin{theo}
@@
 \end{theo}
+}
 
 \section{Weighted Matroid Games}
-Starting from a congestion model where every player aims to buy a basis from
+Starting from a congestion model where every player aims to buy a basis of
 a certain matroid and every player puts an individual demand upon the resources
 she/he uses we derive a complete characterisation of PNEs as well as show that
-every socially optimal solution actually induces a PNE. Firstly, we give some
+every socially optimal solution induces a PNE. First of all, we give some
 auxiliary definitions (with a profile $B\in\mathcal{B}$, a resource $e\in E$):
@@
   \item $\Delta_{i}\tupel{B;e\rightarrow f}$ is the marginal cost player $i$
-    has to pay for resource $f$ if he intends to use $f$ instead of $e$
-    (we define the minimum over all resources $e$ can be exchanged with as
-    $\Delta_{i}^{e}(B) = \min_{f\in\ex_{i}(e)}\Delta_{i}(B;e\rightarrow f)$)
+    has to pay for resource $f$ if he intends to use $f$ instead of $e$.
+    We define the minimum over all resources $e$ can be exchanged with as
+    $\Delta_{i}^{e}(B) = \min_{f\in\ex_{i}(e)}\Delta_{i}(B;e\rightarrow f)$
 \end{itemize}
@@
 \end{theo}
-The \enquote{only if} direction is easily given by the fact that the cost
-of a resource is the sum of the contributions of every player for this resource
-and no player has an incentive to uniliterally change to another basis of
-her/his matroid. While, for the \enquote{if} direction, we let for elements in
-$F$ one player for whom this resource is obligatory pay for this resource
+The \enquote{only if} direction is easily shown by the fact that the cost
+of a resource equals the sum of the contributions of every player for this
+resource and no player has an incentive to unilaterally change to another basis
+of her/his matroid. While, for the \enquote{if} direction, we let for elements
+in $F$ one player for whom this resource is obligatory pay for this resource
 (since she/he needs this resource to be available she/he can not choose to
-uniliterally change her/his payment). For all other elements we can define the
+unilaterally change her/his payment). For all other elements we can define the
 payments as follows:
@@
 
-Using this one can derive a series of inequalities to show that every socially
-optimal solution satisfies the given characterisation and hence
+Using this we can derive a series of inequalities to show that every socially
+optimal solution satisfies the given characterisation and hence:
 \begin{theo}
   Every weighted matroid resource buying game with marginally non-increasing
-  cost functions posses a PNE.
+  cost functions possesses a PNE.
 \end{theo}
@@
 for non-decreasing cost functions. Again starting from a socially optimal
-configuration one can derive a pricing vector (called marginal cost pricing)
-which forms with the given configuration a PNE. Especially this result is
-also viable for non-matroid strategy spaces, yielding:
+configuration we can derive a pricing vector (called marginal cost pricing)
+which forms a PNE with the given configuration. Noteably, this result is
+also true for non-matroid strategy spaces, yielding:
 \begin{theo}
@@
 \section{Non-Matroid Strategy Spaces}
-Finally, we consider in this section non-matroid strategy spaces. Specifically,
-we present a construction which illustrates how to obtain a weighted two player
+Finally, we consider non-matroid strategy spaces. Specifically,
+we present a construction to obtain a weighted two player
 resource buying game with marginally non-increasing cost functions which does
@@
 \begin{theo}
-  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
-  there exists a weighted two-player resource buying game
-  $G = \tupel{\tilde{E},
+  For every non-matroid anti-chain $\mathcal{S}$ (i.e. a family of sets which
+  are not ordered by $\subseteq$) on a set of resources $E$, there exists a
+  weighted two-player resource buying game $G = \tupel{\tilde{E},
     (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
@@
   $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ are both isomorphic to $\mathcal{S}$,
-  so that $G$ does not posses a PNE.
+  so that $G$ does not possess a PNE.
 \end{theo}
-As said before we start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which
+We start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which
 specifically does \emph{not} satisfy the matroid properties. Hence
@@
 \end{lemma}
-Especially we can guarantee that there are two elements in $\mathcal{S}$ s.t.
+Especially, we can guarantee that there are two elements in $\mathcal{S}$ s.t.
 one contains $a$ (but not $b$ and $c$) and the other $b$ and $c$ (but not $a$).
@@
 $\mathcal{S}_{1},\mathcal{S}_{2}$ and by previous lemma there are
-$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We interleaf
-the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by precisely three
-elements $x,y,z$ which we identify in both copies differently. Namely, we set
-$x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and $z = c_{1} = c_{2}$. The set of
-resources for $G$ is now the union of both ground-sets w.r.t. the intersection
-which is $\set{x,y,z}$. Furthermore we fix the cost functions of all elements
-in $\tilde{E}\setminus(X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2})$ to a high constant
-$M$ which ensures that both players only play within $X_{i}, Y_{i}$ (for
-$i = 1,2$ respectively). In this \enquote{sub-arena} we set the cost functions
-of all elements other than $\set{x,y,z}$ to $0$ regardless of the demand. And
-concludingly we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$, and
-$c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and
+$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We
+interleave the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by
+precisely three elements $x,y,z$ which we identify differently in both copies.
+Namely, we set $x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and
+$z = c_{1} = c_{2}$. The set of resources for $G$ is now the union of both
+ground-sets w.r.t. their intersection which is $\set{x,y,z}$. Furthermore, we
+fix the cost functions of all elements in
+$\tilde{E}\setminus(X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2})$ to a high constant
+$M$ which ensures that both players only play within $X_{i},
+Y_{i}$ (for $i = 1,2$ respectively). In this \enquote{sub-arena} we set the
+cost functions of all elements other than $\set{x,y,z}$ to $0$ regardless of
+the demand. And concludingly, we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$,
+and $c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and
 $d_{2} = 4$. Thus, each player either contributes to pay for her/his $a$ or
@@
 \end{equation*}
-By examining the restricted environment of the cost inducing elements ($x,y,z$)
-and the conclusion that one player either only contributes to $x$ or $y$ and
-$z$ and the other only to $y$ or $x$ and $z$ one can conclude that neither
-$x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a contradiction to
-the existence of a PNE and thus concludes the argument on the section-leading
-theorem.
+By examining the restricted environment of the cost inducing elements
+$\set{x,y,z}$ and the conclusion that one player either only contributes to $x$
+or $y$ and $z$ and the other only to $y$ or $x$ and $z$ one can conclude that
+neither $x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a
+contradiction to the existence of a PNE and concludes the argument on the
+theorem proposed at the beginning of the section.
 
@@
 computation of one PNE. For weighted matroid games with marginally
-non-increasing cost functions the existence of PNEs can be assured. Also for
-weighted congestion games with marginally non-decreasing cost functions PNEs
-are given. Hereby the structure of strategy spaces is unrestricted.
+non-increasing cost functions the existence of PNEs can be assured as well as
+for weighted congestion games with marginally non-decreasing cost functions.
+Hereby the structure of strategy spaces is unrestricted.
 Concludingly, marginally non-increasing cost functions demand matroid strategy
-spaces as combinatorial structure which capture e.g. spanning trees, linear
-independence, \dots. On the other hand marginally non-decreasing cost functions
+spaces as combinatorial structures which capture e.g. spanning trees, linear
+independence, etc. On the other hand, marginally non-decreasing cost functions
 might induce a certain stability in a market by ensuring the existence of PNEs.

### 2017-04-07 paper.tex
sent version

@@
 strategic game as well as by introducing matroids as combinatorial structures
-to model desired configurations of resources for players. Following we present
+to model desired configurations of resources for players. Following, we present
 an algorithm to compute PNEs in unweighted matroid games with marginally
@@
 The algorithm we present in the following chooses a basis for every player by
-iteratively adding one element from a cut and contracting the matroid to the
-added element while deleting all other elements from the cut. Since cuts are
-inclusion-wise minimal deleting all but one element from one cut leaves at
-least one possible basis for the player available. For every player we maintain
-the elements which are chosen for her/him up to the current state
+iteratively adding one element from a cut and contracting the matroid of the
+player to the added element while deleting all other elements from the cut.
+Since cuts are inclusion-wise minimal deleting all but one element from one cut
+leaves at least one possible basis for the player available. For every player
+we maintain the elements which are chosen for her/him up to the current state
 (\emph{working basis}) and which elements are still available to build her
@@
 chosen element in step (ii) always decreases. This is a key insight to prove
-the correctness of the algorithm. Because, if we assume to have a beneficial
-alternative to the computed basis for one player there must exist an element
+the correctness of the algorithm because, if we assume to have a beneficial
+alternative to the computed basis for one player, there must exist an element
 with less cost. This alternative element cannot be part of the selected cut
@@
   For every non-matroid anti-chain $\mathcal{S}$ (i.e. a family of sets which
-  are not ordered by $\subseteq$) on a set of resources $E$, there exists a
-  weighted two-player resource buying game $G = \tupel{\tilde{E},
+  are pairwisely not ordered by $\subseteq$) on a set of resources $E$, there
+  exists a weighted two-player resource buying game $G = \tupel{\tilde{E},
     (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
